---
title: "Analyze_real_data"
format: html
editor: visual
---

# Packages

```{r}
list_of_packages <- c(
  "MASS", "ggplot2", "dplyr", "caret", "rpart", "tidyr", "here",
  "glmnet", "synthpop", "purrr", "MonteCarlo", "tidyverse", "Matrix",
  "e1071", "stringr", "bnlearn", "tibble", "gridExtra", "readr")

install_if_missing <- function(p) {
  if (!requireNamespace(p, quietly = TRUE)) install.packages(p)
  library(p, character.only = TRUE)
}

invisible(lapply(list_of_packages, install_if_missing))
```

# Directories

```{r}
data_dir <- here::here("data", "real_data", "data")
figure_dir <- here::here("results", "figures")
table_dir <- here::here("results", "additional_materials")

dir.create(figure_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(table_dir, recursive = TRUE, showWarnings = FALSE)
```

# Compare prediction metrics

```{r}
compare_pred_results <- function(dataset_name,
                                 target_type = c("classification", "regression"),
                                 save_plot = TRUE) {
  target_type <- match.arg(target_type)
  pred_methods <- c("parm", "cart", "bn", "svm")
  synth_methods <- c("parmsyn", "cartsyn", "bnsyn", "svmsyn")
  synth_seeds <- paste0("synmc", 1:5)

  if (target_type == "regression") {
    pred_methods <- setdiff(pred_methods, "bn")
    synth_methods <- setdiff(synth_methods, "bnsyn")
  }

  pred_colors <- c(
    cartpred = "#82c074", bnpred = "#54bdbf",
    parmpred = "#e9496a", svmpred = "#ed9656")
  plot_filename <- paste0("pred_perf_comp_", dataset_name, ".png")
  plot_path <- file.path(figure_dir, plot_filename)

  orig_list <- lapply(pred_methods, function(pred_method) {
    file_path <- file.path(
      data_dir, paste0(dataset_name, "_orig_", pred_method, ".RData"))
    if (!file.exists(file_path)) {
      message("Original file not found: ", file_path)
      return(NULL)
    }
    obj_name <- load(file_path)
    obj <- get(obj_name)
    rm(list = obj_name)
    obj %>%
      mutate(
        dataset = dataset_name, data_type = "original",
        synth_method = "original", synth_seed = NA_character_,
        pred_method = pred_method)
  })
  orig_df <- bind_rows(orig_list)

  syn_list <- list()
  for (synth_method in synth_methods) {
    for (synth_seed in synth_seeds) {
      for (pred_method in pred_methods) {
        file_path <- file.path(
          data_dir,
          paste0(dataset_name, "_", synth_method, "_", synth_seed, "_",
                 pred_method, "pred.RData"))
        if (!file.exists(file_path)) next
        obj_name <- load(file_path)
        obj <- get(obj_name)
        rm(list = obj_name)
        list_name <- paste(synth_method, synth_seed, pred_method, sep = "_")
        syn_list[[list_name]] <- obj %>%
          mutate(
            dataset = dataset_name, data_type = "synthetic",
            synth_method = synth_method, synth_seed = synth_seed,
            pred_method = pred_method)
      }
    }
  }
  syn_df <- bind_rows(syn_list)
  all_df <- bind_rows(orig_df, syn_df)

  id_cols <- c(
    "dataset", "data_type", "synth_method", "synth_seed", "pred_method")
  metric_cols <- setdiff(names(all_df), id_cols)
  synth_levels <- c("original", "parmsyn", "cartsyn", "bnsyn", "svmsyn")
  synth_labels <- c(
    original = "original data", parmsyn = "param. syn.",
    cartsyn = "CART syn.", bnsyn = "BN syn.", svmsyn = "SVM syn.")

  if (target_type == "regression") {
    synth_levels <- c("original", "parmsyn", "cartsyn", "svmsyn")
    synth_labels <- synth_labels[synth_levels]
  }

  plot_df <- all_df %>%
    pivot_longer(
      cols = all_of(metric_cols), names_to = "metric", values_to = "value") %>%
    mutate(
      pred_method_plot = factor(
        paste0(pred_method, "pred"),
        levels = c("parmpred", "cartpred", "bnpred", "svmpred")),
      synth_method = factor(
        synth_method, levels = synth_levels, labels = synth_labels)) %>%
    filter(!is.na(value), metric != "Sensitivity")

  metric_ranges <- plot_df %>%
    group_by(metric) %>%
    summarise(
      ymin = min(value, na.rm = TRUE),
      ymax = max(value, na.rm = TRUE), .groups = "drop") %>%
    tidyr::crossing(
      synth_method = factor(synth_labels, levels = synth_labels),
      pred_method_plot = levels(plot_df$pred_method_plot))

  p <- ggplot(
    plot_df,
    aes(x = pred_method_plot, y = value, color = pred_method_plot)) +
    geom_blank(
      data = metric_ranges, aes(x = pred_method_plot, y = ymin),
      inherit.aes = FALSE) +
    geom_blank(
      data = metric_ranges, aes(x = pred_method_plot, y = ymax),
      inherit.aes = FALSE) +
    geom_jitter(width = 0.24, height = 0, size = 3.2, alpha = 1, shape = 16) +
    facet_grid(metric ~ synth_method, scales = "free_y") +
    scale_color_manual(values = pred_colors, name = "Prediction method") +
    labs(title = NULL, x = NULL, y = "Metric value") +
    theme_minimal(base_size = 13) +
    theme(
      axis.text.x = element_blank(), axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 11),
      axis.title.y = element_text(size = 13),
      legend.title = element_text(size = 12),
      legend.text = element_text(size = 11),
      strip.text = element_text(size = 12, face = "bold"),
      panel.grid.minor = element_blank(),
      panel.spacing.x = grid::unit(0.9, "lines"),
      panel.spacing.y = grid::unit(0.9, "lines"))

  if (save_plot) {
    ggsave(
      filename = plot_path, plot = p,
      width = 12, height = 8, dpi = 300)
  }

  list(
    all_data = all_df, plot_data = plot_df, plot = p,
    plot_path = if (save_plot) plot_path else NA_character_)
}
```

## Adult

```{r}
Adult_comp <- compare_pred_results("Adult", target_type = "classification")
Adult_comp$plot
```

## Bank Marketing

```{r}
BankMarketing_comp <- compare_pred_results(
  "BankMarketing", target_type = "classification")
BankMarketing_comp$plot
```

## Bike Sharing

```{r}
BikeSharing_comp <- compare_pred_results(
  "BikeSharing", target_type = "regression")
BikeSharing_comp$plot
```

## German Credit

```{r}
GermanCredit_comp <- compare_pred_results(
  "GermanCredit", target_type = "classification")
GermanCredit_comp$plot
```

# Compare reinforcement ratio

```{r}
compute_reinforcement_real <- function(
    dataset_name, target_type = c("classification", "regression"),
    save_plot = TRUE) {
  target_type <- match.arg(target_type)
  higher_better <- c(
    "Accuracy", "F1", "Specificity", "Sensitivity", "R_squared")
  lower_better <- c("RMSE", "MAE")
  pred_methods <- c("parm", "cart", "bn", "svm")
  synth_methods <- c("parmsyn", "cartsyn", "bnsyn", "svmsyn")
  synth_seeds <- paste0("synmc", 1:5)

  if (target_type == "regression") {
    synth_methods <- setdiff(synth_methods, "bnsyn")
  }

  family_from_model <- function(x) {
    dplyr::case_when(
      stringr::str_detect(x, "^cart") ~ "cart",
      stringr::str_detect(x, "^svm") ~ "svm",
      stringr::str_detect(x, "^parm") ~ "parm",
      stringr::str_detect(x, "^bn") ~ "bn",
      TRUE ~ NA_character_)
  }

  family_palette <- c(
    cart = "#82c074", bn = "#54bdbf",
    parm = "#e9496a", svm = "#ed9656")
  family_labels <- c(
    parm = "Parametric Syn.", cart = "CART Syn.",
    bn = "BN Syn.", svm = "SVM Syn.")
  family_order <- c("parm", "cart", "bn", "svm")

  if (target_type == "regression") {
    family_order <- setdiff(family_order, "bn")
    family_labels <- family_labels[family_order]
  }

  orig_list <- lapply(pred_methods, function(pred_method) {
    file_path <- file.path(
      data_dir, paste0(dataset_name, "_orig_", pred_method, ".RData"))
    if (!file.exists(file_path)) {
      message("Original file not found: ", file_path)
      return(NULL)
    }
    obj_name <- load(file_path)
    obj <- get(obj_name)
    rm(list = obj_name)
    obj %>%
      mutate(
        dataset = dataset_name, data_type = "original",
        synth_method = NA_character_, synth_seed = NA_character_,
        Prediction_Model = paste0(pred_method, "pred"),
        Synthesis_Model = NA_character_)
  })
  orig_df <- bind_rows(orig_list)

  syn_list <- list()
  for (synth_method in synth_methods) {
    for (synth_seed in synth_seeds) {
      for (pred_method in pred_methods) {
        file_path <- file.path(
          data_dir,
          paste0(dataset_name, "_", synth_method, "_", synth_seed, "_",
                 pred_method, "pred.RData"))
        if (!file.exists(file_path)) next
        obj_name <- load(file_path)
        obj <- get(obj_name)
        rm(list = obj_name)
        list_name <- paste(synth_method, synth_seed, pred_method, sep = "_")
        syn_list[[list_name]] <- obj %>%
          mutate(
            dataset = dataset_name, data_type = "synthetic",
            synth_method = synth_method, synth_seed = synth_seed,
            Prediction_Model = paste0(pred_method, "pred"),
            Synthesis_Model = synth_method)
      }
    }
  }
  syn_df <- bind_rows(syn_list)

  all_df <- bind_rows(orig_df, syn_df)
  id_cols <- c(
    "dataset", "data_type", "synth_method", "synth_seed",
    "Prediction_Model", "Synthesis_Model")
  metric_cols <- setdiff(names(all_df), id_cols)

  long_df <- all_df %>%
    pivot_longer(
      cols = all_of(metric_cols), names_to = "Metric", values_to = "Value") %>%
    filter(!is.na(Value)) %>%
    mutate(
      TargetType = ifelse(
        target_type == "regression", "Continuous", "Categorical"),
      Synth_Family = family_from_model(Synthesis_Model),
      Pred_Family = family_from_model(Prediction_Model))

  if (target_type == "regression") {
    long_df <- long_df %>%
      filter(Pred_Family != "bn") %>%
      filter(Synth_Family != "bn" | is.na(Synth_Family))
  }

  orig_rel <- long_df %>%
    filter(data_type == "original") %>%
    group_by(dataset, Metric) %>%
    mutate(
      best_val = case_when(
        Metric %in% higher_better ~ max(Value, na.rm = TRUE),
        Metric %in% lower_better ~ min(Value, na.rm = TRUE),
        TRUE ~ NA_real_),
      rel_orig = case_when(
        Metric %in% higher_better ~ Value / best_val,
        Metric %in% lower_better ~ best_val / Value,
        TRUE ~ NA_real_)) %>%
    ungroup() %>%
    dplyr::select(
      dataset, Metric, Pred_Family, Prediction_Model, rel_orig)

  synth_rel <- long_df %>%
    filter(data_type == "synthetic") %>%
    group_by(dataset, synth_method, synth_seed, Metric) %>%
    mutate(
      best_val = case_when(
        Metric %in% higher_better ~ max(Value, na.rm = TRUE),
        Metric %in% lower_better ~ min(Value, na.rm = TRUE),
        TRUE ~ NA_real_),
      rel_synth = case_when(
        Metric %in% higher_better ~ Value / best_val,
        Metric %in% lower_better ~ best_val / Value,
        TRUE ~ NA_real_)) %>%
    ungroup() %>%
    dplyr::select(
      dataset, synth_method, synth_seed, Metric, Synth_Family,
      Pred_Family, Prediction_Model, rel_synth)

  synth_same <- synth_rel %>%
    filter(Synth_Family == Pred_Family)

  reinforce <- synth_same %>%
    left_join(
      orig_rel %>%
        dplyr::select(dataset, Metric, Pred_Family, rel_orig),
      by = c("dataset", "Metric", "Pred_Family")) %>%
    mutate(Reinforcement = rel_synth / rel_orig)

  reinforce_avg <- reinforce %>%
    group_by(dataset, Metric, Synth_Family) %>%
    summarise(
      Reinforcement = mean(Reinforcement, na.rm = TRUE),
      .groups = "drop") %>%
    mutate(Synth_Family = factor(Synth_Family, levels = family_order))

  plot_reinforcement <- function(metric_name) {
    df_sub <- reinforce %>%
      filter(Metric == metric_name) %>%
      mutate(Synth_Family = factor(Synth_Family, levels = family_order))

    if (nrow(df_sub) == 0) return(ggplot() + theme_void())

    p <- ggplot(
      df_sub,
      aes(x = Synth_Family, y = Reinforcement, color = Synth_Family)) +
      geom_jitter(
        width = 0.12, height = 0, size = 3.2, alpha = 1, shape = 16) +
      geom_hline(yintercept = 1, linetype = "dotted") +
      scale_color_manual(
        values = family_palette[family_order], breaks = family_order,
        labels = family_labels[family_order], name = "Synthesis model") +
      scale_x_discrete(labels = family_labels[family_order]) +
      labs(title = NULL, x = NULL, y = "R") +
      theme_minimal(base_size = 13) +
      theme(
        axis.text.x = element_text(size = 11, angle = 20, hjust = 1),
        axis.text.y = element_text(size = 11),
        axis.title.y = element_text(size = 13),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 11),
        panel.grid.minor = element_blank())

    if (save_plot) {
      plot_filename <- paste0(
        "reinf_", dataset_name, "_", metric_name, ".png")
      plot_path <- file.path(figure_dir, plot_filename)
      ggsave(
        filename = plot_path, plot = p,
        width = 8, height = 6, dpi = 300)
    }
    p
  }

  list(
    long_data = long_df, reinforce = reinforce,
    reinforce_avg = reinforce_avg, plot_metric = plot_reinforcement)
}
```

## Adult

```{r}
Adult_reinf <- compute_reinforcement_real(
  "Adult", target_type = "classification")
Adult_reinf$plot_metric("Accuracy")
Adult_reinf$plot_metric("F1")
Adult_reinf$plot_metric("Specificity")
#Adult_reinf$plot_metric("Sensitivity")
```

## Bank Marketing

```{r}
BankMarketing_reinf <- compute_reinforcement_real(
  "BankMarketing", target_type = "classification")
BankMarketing_reinf$plot_metric("Accuracy")
BankMarketing_reinf$plot_metric("F1")
BankMarketing_reinf$plot_metric("Specificity")
#BankMarketing_reinf$plot_metric("Sensitivity")
```

## Bike Sharing

```{r}
BikeSharing_reinf <- compute_reinforcement_real(
  "BikeSharing", target_type = "regression")
BikeSharing_reinf$plot_metric("RMSE")
BikeSharing_reinf$plot_metric("R_squared")
BikeSharing_reinf$plot_metric("MAE")
```

## German Credit

```{r}
GermanCredit_reinf <- compute_reinforcement_real(
  "GermanCredit", target_type = "classification")
GermanCredit_reinf$plot_metric("Accuracy")
GermanCredit_reinf$plot_metric("F1")
GermanCredit_reinf$plot_metric("Specificity")
#GermanCredit_reinf$plot_metric("Sensitivity")
```

# Save numeric prediction values

The following table contains every metric value used in the real-data figures and ranking analysis, separately for the original and synthetic datasets.

```{r}
reinforcement_results <- list(
  Adult = Adult_reinf,
  BankMarketing = BankMarketing_reinf,
  BikeSharing = BikeSharing_reinf,
  GermanCredit = GermanCredit_reinf)

real_prediction_values <- reinforcement_results %>%
  purrr::map_dfr("long_data") %>%
  mutate(
    Synthesis_Model = if_else(
      data_type == "original", "original", Synthesis_Model)) %>%
  dplyr::select(
    dataset, TargetType, data_type, synth_method, synth_seed,
    Synthesis_Model, Synth_Family, Prediction_Model, Pred_Family,
    Metric, Value) %>%
  arrange(
    dataset, Metric, data_type, Synthesis_Model,
    synth_seed, Prediction_Model)

readr::write_csv(
  real_prediction_values,
  file.path(table_dir, "real_data_prediction_values.csv"))

print(real_prediction_values, n = 40)
```

# Ranking and model-selection metrics

Top-1 agreement is true when the original and synthetic rankings share at least one best-performing model. This definition handles exact ties without arbitrarily selecting one of the tied models. A ranking reversal therefore means that the two sets of best-performing models do not overlap.

```{r}
safe_cor <- function(x, y, method = "spearman") {
  ok <- complete.cases(x, y)
  if (sum(ok) < 2) return(NA_real_)
  if (length(unique(x[ok])) < 2) return(NA_real_)
  if (length(unique(y[ok])) < 2) return(NA_real_)
  tryCatch(
    suppressWarnings(cor(x[ok], y[ok], method = method)),
    error = function(e) NA_real_)
}

compute_ranking_real <- function(
    long_df, target_type = c("classification", "regression")) {
  target_type <- match.arg(target_type)
  higher_better <- c(
    "Accuracy", "F1", "Specificity", "Sensitivity", "R_squared")
  lower_better <- c("RMSE", "MAE")

  family_from_model <- function(x) {
    dplyr::case_when(
      stringr::str_detect(x, "^cart") ~ "cart",
      stringr::str_detect(x, "^svm") ~ "svm",
      stringr::str_detect(x, "^parm") ~ "parm",
      stringr::str_detect(x, "^bn") ~ "bn",
      TRUE ~ NA_character_)
  }

  rank_df <- long_df %>%
    mutate(
      Pred_Family = family_from_model(Prediction_Model),
      Synth_Family = family_from_model(Synthesis_Model))

  if (target_type == "regression") {
    rank_df <- rank_df %>%
      filter(Pred_Family != "bn") %>%
      filter(Synth_Family != "bn" | is.na(Synth_Family))
  }

  orig_rank <- rank_df %>%
    filter(data_type == "original") %>%
    group_by(dataset, Metric) %>%
    mutate(
      rank_orig = case_when(
        first(Metric) %in% higher_better ~
          rank(-Value, ties.method = "average"),
        first(Metric) %in% lower_better ~
          rank(Value, ties.method = "average"),
        TRUE ~ NA_real_),
      best_rank_orig = min(rank_orig, na.rm = TRUE),
      best_orig = rank_orig == best_rank_orig) %>%
    ungroup() %>%
    dplyr::select(
      dataset, Metric, Prediction_Model, Pred_Family,
      value_orig = Value, rank_orig, best_orig)

  synth_rank <- rank_df %>%
    filter(data_type == "synthetic") %>%
    group_by(dataset, synth_method, synth_seed, Synth_Family, Metric) %>%
    mutate(
      rank_synth = case_when(
        first(Metric) %in% higher_better ~
          rank(-Value, ties.method = "average"),
        first(Metric) %in% lower_better ~
          rank(Value, ties.method = "average"),
        TRUE ~ NA_real_),
      best_rank_synth = min(rank_synth, na.rm = TRUE),
      best_synth = rank_synth == best_rank_synth) %>%
    ungroup() %>%
    dplyr::select(
      dataset, synth_method, synth_seed, Synth_Family, Metric,
      Prediction_Model, Pred_Family, value_synth = Value,
      rank_synth, best_synth)

  rank_compare <- synth_rank %>%
    left_join(
      orig_rank,
      by = c("dataset", "Metric", "Prediction_Model", "Pred_Family"))

  ranking_metrics <- rank_compare %>%
    group_by(dataset, synth_method, synth_seed, Synth_Family, Metric) %>%
    summarise(
      best_orig_models = paste(
        sort(unique(Prediction_Model[best_orig %in% TRUE])), collapse = ";"),
      best_synth_models = paste(
        sort(unique(Prediction_Model[best_synth %in% TRUE])), collapse = ";"),
      n_best_orig = sum(best_orig, na.rm = TRUE),
      n_best_synth = sum(best_synth, na.rm = TRUE),
      top1_agreement = any(best_orig & best_synth, na.rm = TRUE),
      synthetic_best_is_same_family = any(
        best_synth & Pred_Family == Synth_Family, na.rm = TRUE),
      original_best_is_synth_family = any(
        best_orig & Pred_Family == Synth_Family, na.rm = TRUE),
      synth_family_rank_orig = dplyr::first(
        rank_orig[Pred_Family == Synth_Family], default = NA_real_),
      synth_family_rank_synth = dplyr::first(
        rank_synth[Pred_Family == Synth_Family], default = NA_real_),
      spearman_rho = safe_cor(rank_orig, rank_synth, method = "spearman"),
      kendall_tau = safe_cor(rank_orig, rank_synth, method = "kendall"),
      .groups = "drop") %>%
    mutate(
      ranking_reversal = !top1_agreement,
      reversal_to_synth_family =
        ranking_reversal & synthetic_best_is_same_family,
      synth_family_becomes_winner =
        synthetic_best_is_same_family & !original_best_is_synth_family,
      synth_family_rank_change =
        synth_family_rank_synth - synth_family_rank_orig)

  ranking_summary <- ranking_metrics %>%
    group_by(dataset, synth_method, Synth_Family, Metric) %>%
    summarise(
      n_cases = n(),
      n_same_best = sum(top1_agreement, na.rm = TRUE),
      same_best_rate = mean(top1_agreement, na.rm = TRUE),
      n_different_best = sum(ranking_reversal, na.rm = TRUE),
      different_best_rate = mean(ranking_reversal, na.rm = TRUE),
      n_synthetic_best_same_family = sum(
        synthetic_best_is_same_family, na.rm = TRUE),
      synthetic_best_same_family_rate = mean(
        synthetic_best_is_same_family, na.rm = TRUE),
      n_reversals_to_synth_family = sum(
        reversal_to_synth_family, na.rm = TRUE),
      share_reversals_to_synth_family = if_else(
        n_different_best > 0,
        n_reversals_to_synth_family / n_different_best, NA_real_),
      n_synth_family_becomes_winner = sum(
        synth_family_becomes_winner, na.rm = TRUE),
      synth_family_becomes_winner_rate = mean(
        synth_family_becomes_winner, na.rm = TRUE),
      mean_synth_family_rank_change = mean(
        synth_family_rank_change, na.rm = TRUE),
      spearman_rho = mean(spearman_rho, na.rm = TRUE),
      kendall_tau = mean(kendall_tau, na.rm = TRUE),
      .groups = "drop")

  list(
    rank_compare = rank_compare,
    ranking_metrics = ranking_metrics,
    ranking_summary = ranking_summary)
}
```

```{r}
datasets <- c("Adult", "BankMarketing", "BikeSharing", "GermanCredit")
target_types <- c(
  Adult = "classification", BankMarketing = "classification",
  BikeSharing = "regression", GermanCredit = "classification")

ranking_results <- purrr::map(datasets, function(ds) {
  compute_ranking_real(
    long_df = reinforcement_results[[ds]]$long_data,
    target_type = target_types[[ds]])
})
names(ranking_results) <- datasets

all_rank_comparisons <- purrr::map_dfr(ranking_results, "rank_compare")
all_ranking_metrics <- purrr::map_dfr(ranking_results, "ranking_metrics")
all_ranking_real <- purrr::map_dfr(ranking_results, "ranking_summary")
```

## Overall model-selection summary

```{r}
summarise_model_selection <- function(data) {
  data %>%
    summarise(
      n_cases = n(),
      n_same_best = sum(top1_agreement, na.rm = TRUE),
      same_best_rate = mean(top1_agreement, na.rm = TRUE),
      n_different_best = sum(ranking_reversal, na.rm = TRUE),
      different_best_rate = mean(ranking_reversal, na.rm = TRUE),
      n_synthetic_best_same_family = sum(
        synthetic_best_is_same_family, na.rm = TRUE),
      synthetic_best_same_family_rate = mean(
        synthetic_best_is_same_family, na.rm = TRUE),
      n_reversals_to_synth_family = sum(
        reversal_to_synth_family, na.rm = TRUE),
      share_reversals_to_synth_family = if_else(
        n_different_best > 0,
        n_reversals_to_synth_family / n_different_best, NA_real_),
      n_synth_family_becomes_winner = sum(
        synth_family_becomes_winner, na.rm = TRUE),
      synth_family_becomes_winner_rate = mean(
        synth_family_becomes_winner, na.rm = TRUE))
}

ranking_overall <- summarise_model_selection(all_ranking_metrics)

ranking_by_dataset <- all_ranking_metrics %>%
  group_by(dataset) %>%
  group_modify(~ summarise_model_selection(.x)) %>%
  ungroup()

ranking_by_dataset_and_synthesis <- all_ranking_metrics %>%
  group_by(dataset, synth_method, Synth_Family) %>%
  group_modify(~ summarise_model_selection(.x)) %>%
  ungroup()

print(ranking_overall)
print(ranking_by_dataset, n = Inf)
print(ranking_by_dataset_and_synthesis, n = Inf)
```

# Save ranking tables

```{r}
readr::write_csv(
  all_rank_comparisons,
  file.path(table_dir, "real_data_rank_comparisons.csv"))
readr::write_csv(
  all_ranking_metrics,
  file.path(table_dir, "real_data_ranking_metrics.csv"))
readr::write_csv(
  all_ranking_real,
  file.path(table_dir, "real_data_ranking_summary.csv"))
readr::write_csv(
  ranking_overall,
  file.path(table_dir, "real_data_ranking_overall.csv"))
readr::write_csv(
  ranking_by_dataset,
  file.path(table_dir, "real_data_ranking_by_dataset.csv"))
readr::write_csv(
  ranking_by_dataset_and_synthesis,
  file.path(table_dir, "real_data_ranking_by_dataset_and_synthesis.csv"))
```
