---
title: "Reinforcement analysis"
date: "`r Sys.Date()`"
---

This document evaluates whether synthetic data systematically improve the
relative position of prediction models from the same family as the synthesis
model. All comparisons are made against the corresponding prediction-model
performance on the original data.

The analysis has three complementary parts:

1. the original same-family reinforcement ratio;
2. the full synthesis-family by prediction-family matrix; and
3. a diagonal contrast testing whether matching prediction models improve more
   than nonmatching prediction models.

# Setup

```{r setup, message=FALSE, warning=FALSE}
packages <- c(
  "dplyr", "tidyr", "purrr", "stringr", "ggplot2", "readr",
  "tibble", "here")
missing_packages <- packages[!vapply(packages, requireNamespace, logical(1),
                                     quietly = TRUE)]
if (length(missing_packages) > 0) {
  stop("Install the following packages first: ",
       paste(missing_packages, collapse = ", "))
}
invisible(lapply(packages, library, character.only = TRUE))
```

```{r}
# Configuration for sequential execution in RStudio.
data_dir <- here::here("data")
figure_dir <- here::here("results", "figures")
table_dir <- here::here("results", "additional_materials")
 
dir.create(data_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(figure_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(table_dir, recursive = TRUE, showWarnings = FALSE)
 
data_file <- file.path(data_dir, "combined_long.RData")
bootstrap_reps <- 4999L
permutation_reps <- 4999L
random_seed <- 1234L
set.seed(random_seed)
```

## Load the combined results

```{r load-data}
data_path <- if (file.exists(data_file)) {
  normalizePath(data_file)
} else {
  here::here(data_file)
}
if (!file.exists(data_path)) stop("Data file not found: ", data_path)

data_environment <- new.env(parent = emptyenv())
loaded_objects <- load(data_path, envir = data_environment)
if (!"combined_long" %in% loaded_objects) {
  stop("The input file must contain an object named 'combined_long'.")
}
combined_long <- get("combined_long", envir = data_environment)
rm(data_environment)

required_columns <- c(
  "Parameter_Set", "Target", "Metric", "Value",
  "Synthesis_Model", "Prediction_Model")
missing_columns <- setdiff(required_columns, names(combined_long))
if (length(missing_columns) > 0) {
  stop("Missing required columns: ", paste(missing_columns, collapse = ", "))
}
if (!"TargetType" %in% names(combined_long)) combined_long$TargetType <- NA_character_
if (!"Data_Type" %in% names(combined_long)) combined_long$Data_Type <- NA_character_
```

# Definitions and helper functions

```{r definitions}
higher_better <- c("Accuracy", "F1", "Specificity", "R_squared")
lower_better <- c("RMSE", "MAE")
valid_metrics <- c(higher_better, lower_better)
continuous_metrics <- c("R_squared", "RMSE", "MAE")
categorical_metrics <- c("Accuracy", "F1", "Specificity")

family_order <- c("parm", "cart", "svm", "bn")
family_labels <- c(
  parm = "Parametric", cart = "CART", svm = "SVM", bn = "BN")
family_palette <- c(
  parm = "#E9496A", cart = "#82C074", svm = "#ED9656", bn = "#54BDBF")
data_type_labels <- c(
  hierarchical = "Hierarchical simulation",
  parametric = "Parametric simulation")
metric_labels <- c(
  R_squared = expression(R^2), RMSE = "RMSE", MAE = "MAE",
  Accuracy = "Accuracy", F1 = "F1", Specificity = "Specificity")

targets_by_p <- list(
  `6` = c("X1", "X2", "X3", "C1", "C2", "C3"),
  `12` = c("X2", "X4", "X6", "C2", "C4", "C6"),
  `18` = c("X3", "X6", "X9", "C3", "C6", "C9"))

extract_index <- function(x, prefix) {
  # This intentionally reproduces the extraction used in the original script.
  pattern <- paste0(prefix, "(\\d+)")
  suppressWarnings(as.integer(stringr::str_match(x, pattern)[, 2]))
}

family_from_model <- function(x) {
  dplyr::case_when(
    stringr::str_detect(x, "^parm") ~ "parm",
    stringr::str_detect(x, "^cart") ~ "cart",
    stringr::str_detect(x, "^svm") ~ "svm",
    stringr::str_detect(x, "^bn") ~ "bn",
    TRUE ~ NA_character_)
}

is_selected_target <- function(p, target) {
  purrr::map2_lgl(p, target, function(p_i, target_i) {
    target_i %in% targets_by_p[[as.character(p_i)]]
  })
}

relativize <- function(data) {
  data %>%
    # Keep these groups identical to the original analysis. In particular,
    # Parameter_Set distinguishes the original and synthetic datasets.
    group_by(Data_Type, Synthesis_Model, Parameter_Set, Target, Metric) %>%
    mutate(
      best_val = case_when(
        Metric %in% higher_better ~ max(Value, na.rm = TRUE),
        Metric %in% lower_better ~ min(Value, na.rm = TRUE),
        TRUE ~ NA_real_
      ),
      rel = case_when(
        Metric %in% c("Accuracy", "F1", "Specificity") & best_val > 0 ~
          Value / best_val,
        Metric %in% c("Accuracy", "F1", "Specificity") & best_val == 0 ~ 1,
        Metric == "R_squared" & 1 - best_val > .Machine$double.eps ~
          (1 - best_val) / (1 - Value),
        Metric == "R_squared" & abs(1 - best_val) <= .Machine$double.eps &
          abs(Value - best_val) <= .Machine$double.eps ~ 1,
        Metric == "R_squared" & abs(1 - best_val) <= .Machine$double.eps ~ 0,
        Metric %in% lower_better & best_val > 0 ~ best_val / Value,
        Metric %in% lower_better & best_val == 0 & Value == 0 ~ 1,
        Metric %in% lower_better & best_val == 0 ~ 0,
        TRUE ~ NA_real_)
    ) %>%
    ungroup()
}

bootstrap_mean_summary <- function(x, reps = bootstrap_reps,
                                   seed = random_seed) {
  x <- x[is.finite(x)]
  n <- length(x)
  if (n == 0) {
    return(tibble(
      n_clusters = 0L, estimate = NA_real_, std_error = NA_real_,
      conf_low = NA_real_, conf_high = NA_real_, p_boot = NA_real_))
  }
  if (n == 1) {
    return(tibble(
      n_clusters = 1L, estimate = x, std_error = NA_real_,
      conf_low = NA_real_, conf_high = NA_real_, p_boot = NA_real_))
  }

  set.seed(seed)
  boot_means <- replicate(reps, mean(sample(x, n, replace = TRUE)))
  p_lower <- (sum(boot_means <= 0) + 1) / (reps + 1)
  p_upper <- (sum(boot_means >= 0) + 1) / (reps + 1)
  tibble(
    n_clusters = n,
    estimate = mean(x),
    std_error = sd(boot_means),
    conf_low = unname(quantile(boot_means, 0.025)),
    conf_high = unname(quantile(boot_means, 0.975)),
    p_boot = min(1, 2 * min(p_lower, p_upper)))
}

safe_rank_correlation <- function(x, y, method = "spearman") {
  keep <- complete.cases(x, y)
  if (sum(keep) < 2 || length(unique(x[keep])) < 2 ||
      length(unique(y[keep])) < 2) return(NA_real_)
  suppressWarnings(cor(x[keep], y[keep], method = method))
}
```

# Prepare the analysis data

```{r prepare-data}
dat <- combined_long %>%
  mutate(
    p = extract_index(Parameter_Set, "p"),
    mc = extract_index(Parameter_Set, "mc"),
    synmc = extract_index(Parameter_Set, "synmc"),
    TargetType = ifelse(
      is.na(TargetType),
      ifelse(stringr::str_starts(Target, "X"), "Continuous", "Categorical"),
      TargetType
    ),
    Data_Type = ifelse(
      is.na(Data_Type),
      ifelse(
        stringr::str_detect(Synthesis_Model, "hier"),
        "hierarchical", "parametric"
      ),
      Data_Type
    ),
    Data_Type = dplyr::recode(Data_Type, linear = "parametric"),
    Synth_Family = family_from_model(Synthesis_Model),
    Pred_Family = family_from_model(Prediction_Model)
  ) %>%
  filter(
    !(Prediction_Model == "bnpred" & TargetType == "Continuous"),
    !(stringr::str_detect(Synthesis_Model, "^bn") &
        TargetType == "Continuous")
  )

orig_df <- dat %>% filter(is.na(synmc))
synth_df <- dat %>% filter(!is.na(synmc))

orig_rel <- relativize(orig_df)
synth_rel <- relativize(synth_df)

score_check <- bind_rows(orig_rel, synth_rel) %>%
  summarise(
    n = n(),
    n_missing = sum(is.na(rel)),
    min_score = min(rel, na.rm = TRUE),
    max_score = max(rel, na.rm = TRUE))
print(score_check)
```

The relative score is one for the best prediction model in a dataset and lies
between zero and one for the remaining models. For (R^2), the score is based
on unexplained variation, ((1-R^2_{\mathrm{best}})/(1-R^2_m)), so negative
values of (R^2) remain admissible.

## Match original and synthetic results

```{r match-results}
comparison_keys <- c(
  "Data_Type", "p", "mc", "TargetType", "Target", "Metric", "Pred_Family")

orig_all <- orig_rel %>%
  filter(Pred_Family %in% c("cart", "svm", "parm", "bn")) %>%
  dplyr::select(all_of(comparison_keys), value_orig = Value,
         rel_orig = rel)

synth_same <- synth_rel %>%
  filter(Pred_Family == Synth_Family) %>%
  dplyr::select(
    all_of(comparison_keys), synmc, Synthesis_Model, Synth_Family,
    value_synth = Value, rel_synth = rel)

# This is the original same-family join. Missing matches are left as NA and
# handled by mean(..., na.rm = TRUE), exactly as in the initial script.
reinforce <- synth_same %>%
  left_join(orig_all, by = comparison_keys) %>%
  mutate(Reinforcement = rel_synth / rel_orig) %>%
  filter(is_selected_target(p, Target))

same_family_ratio <- reinforce %>%
  mutate(
    reinforcement_ratio = Reinforcement,
    same_family = TRUE
  )

reinforce_avg <- reinforce %>%
  group_by(Data_Type, p, mc, Metric, TargetType, Synth_Family, Target) %>%
  summarise(Reinforcement = mean(Reinforcement, na.rm = TRUE), .groups = "drop")

metrics_cont <- reinforce_avg %>%
  filter(TargetType == "Continuous") %>%
  distinct(Metric) %>%
  pull(Metric)
metrics_cat <- reinforce_avg %>%
  filter(TargetType == "Categorical") %>%
  distinct(Metric) %>%
  pull(Metric)

print(
  reinforce %>%
    count(Data_Type, TargetType, Synth_Family, name = "n") %>%
    arrange(Data_Type, TargetType, Synth_Family),
  n = Inf
)
```

# Same-family reinforcement ratio

This reproduces the original analysis. For each synthesis method, it compares
the relative-to-best score of the matching prediction model on synthetic and
original data:

\[
R_{s} = \frac{\operatorname{rel}^{\mathrm{syn}}_{s,s}}
              {\operatorname{rel}^{\mathrm{orig}}_{s}}.
\]

Values above one indicate that the matching prediction model moved closer to
the best-performing model after synthesis.

```{r same-family-ratio}
plot_one_panel_avg <- function(data, metric_name, target_type_label) {
  plot_data <- data %>%
    filter(
      Metric == metric_name,
      TargetType == target_type_label,
      is.finite(Reinforcement)
    )
 
  if (nrow(plot_data) == 0) {
    return(
      ggplot() +
        labs(subtitle = "No data for this combination") +
        theme_void()
    )
  }
 
  is_continuous <- target_type_label == "Continuous"
 
  if (is_continuous &&
      metric_name %in% c("RMSE", "R_squared", "MAE")) {
    y_min_plot <- 0.5
    y_max_plot <- 20
 
  } else if (is_continuous) {
    y_min <- min(plot_data$Reinforcement, na.rm = TRUE)
    y_max <- max(plot_data$Reinforcement, na.rm = TRUE)
    y_pad <- 0.05 * (y_max - y_min)
 
    if (!is.finite(y_pad) || y_pad == 0) {
      y_pad <- 0.05
    }
 
    y_min_plot <- y_min - y_pad
    y_max_plot <- y_max + y_pad
 
  } else if (metric_name %in% c("Accuracy", "F1")) {
    scale_data <- plot_data %>%
      filter(Data_Type == "hierarchical")
 
    y_min <- min(scale_data$Reinforcement, na.rm = TRUE)
    y_max <- max(scale_data$Reinforcement, na.rm = TRUE)
    y_pad <- 0.05 * (y_max - y_min)
 
    if (!is.finite(y_pad) || y_pad == 0) {
      y_pad <- 0.05
    }
 
    y_min_plot <- y_min - y_pad
    y_max_plot <- y_max + y_pad
 
  } else if (metric_name == "Specificity") {
    y_min_plot <- 0.7
    y_max_plot <- 2.2
 
  } else {
    y_min <- min(plot_data$Reinforcement, na.rm = TRUE)
    y_max <- max(plot_data$Reinforcement, na.rm = TRUE)
    y_pad <- 0.05 * (y_max - y_min)
 
    if (!is.finite(y_pad) || y_pad == 0) {
      y_pad <- 0.05
    }
 
    y_min_plot <- y_min - y_pad
    y_max_plot <- y_max + y_pad
  }
 
  plot_data <- plot_data %>%
    mutate(
      Synth_Family = factor(
        Synth_Family,
        levels = family_order
      ),
      is_outlier = Reinforcement < y_min_plot |
        Reinforcement > y_max_plot,
      clipped_side = case_when(
        Reinforcement > y_max_plot ~ "upper",
        Reinforcement < y_min_plot ~ "lower",
        TRUE ~ "inside"
      )
    )
 
  inside <- plot_data %>%
    filter(!is_outlier)
 
  outliers <- plot_data %>%
    filter(is_outlier) %>%
    mutate(
      Reinforcement_clipped = case_when(
        clipped_side == "upper" ~ y_max_plot,
        clipped_side == "lower" ~ y_min_plot
      ),
      outlier_label_single = format(
        round(Reinforcement, 2),
        nsmall = 2
      )
    ) %>%
    group_by(
      Data_Type,
      p,
      mc,
      Metric,
      TargetType,
      Synth_Family,
      clipped_side
    ) %>%
    summarise(
      Reinforcement_clipped = first(Reinforcement_clipped),
      outlier_label = paste(
        outlier_label_single,
        collapse = "\n"
      ),
      .groups = "drop"
    ) %>%
    mutate(
      label_y = case_when(
        clipped_side == "upper" ~
          Reinforcement_clipped -
          0.06 * (y_max_plot - y_min_plot),
        clipped_side == "lower" ~
          Reinforcement_clipped +
          0.06 * (y_max_plot - y_min_plot)
      ),
      x_outlier = as.numeric(factor(mc)) +
        case_when(
          Synth_Family %in% c("bn", "parm") ~ -0.24,
          Synth_Family == "cart" ~ 0.08,
          Synth_Family == "svm" ~ 0.24,
          TRUE ~ 0
        )
    )
 
  ggplot(
    inside,
    aes(
      x = factor(mc),
      y = Reinforcement,
      color = Synth_Family
    )
  ) +
    geom_point(
      position = position_dodge(width = 0.7),
      size = 2.5
    ) +
    geom_point(
      data = outliers,
      aes(
        x = x_outlier,
        y = Reinforcement_clipped,
        color = Synth_Family
      ),
      size = 2.5,
      alpha = 0.3,
      inherit.aes = FALSE
    ) +
    geom_text(
      data = outliers,
      aes(
        x = x_outlier,
        y = label_y,
        label = outlier_label,
        color = Synth_Family
      ),
      size = 2,
      lineheight = 1,
      show.legend = FALSE,
      inherit.aes = FALSE
    ) +
    facet_grid(
      rows = vars(Data_Type),
      cols = vars(p),
      scales = "fixed",
      labeller = labeller(
        Data_Type = data_type_labels
      )
    ) +
    geom_hline(
      yintercept = 1,
      linetype = "dotted"
    ) +
    scale_color_manual(
      values = family_palette,
      breaks = family_order,
      labels = family_labels,
      name = "Synthesis model"
    ) +
    coord_cartesian(
      ylim = c(y_min_plot, y_max_plot),
      clip = "off"
    ) +
    labs(
      x = paste(
        "simulation replication per type of simulation and",
        "number of variables"
      ),
      y = "R"
    ) +
    theme(
      axis.text.x = element_text(
        angle = 0,
        hjust = 0.5
      ),
      plot.margin = margin(5.5, 30, 5.5, 5.5)
    )
}
 
for (metric_name in metrics_cont) {
  plot <- plot_one_panel_avg(
    reinforce_avg,
    metric_name,
    "Continuous"
  )
 
  print(plot)
 
  ggsave(
    file.path(
      figure_dir,
      paste0(
        "Reinforcement_avgSynmc_",
        metric_name,
        "_Continuous.png"
      )
    ),
    plot,
    width = 11,
    height = 6,
    dpi = 300
  )
}
 
for (metric_name in metrics_cat) {
  plot <- plot_one_panel_avg(
    reinforce_avg,
    metric_name,
    "Categorical"
  )
 
  print(plot)
 
  ggsave(
    file.path(
      figure_dir,
      paste0(
        "Reinforcement_avgSynmc_",
        metric_name,
        "_Categorical.png"
      )
    ),
    plot,
    width = 11,
    height = 6,
    dpi = 300
  )
}
```

# Full synthesis-by-prediction matrix

The reinforcement ratio considers only the prediction model matching the
synthesizer. To determine whether the matching model is uniquely favored, the
following analysis retains every synthesis-by-prediction combination. For
synthesis family (s) and prediction family (m), define

\[
\Delta_{s,m} =
\operatorname{rel}^{\mathrm{syn}}_{s,m}
- \operatorname{rel}^{\mathrm{orig}}_{m}.
\]

A positive value means that prediction model (m) moved closer to the best
model after synthesis by (s). A same-family reinforcement mechanism predicts
that diagonal cells, where (s=m), are more positive than off-diagonal cells.

## Construct and summarize the matrix

```{r reinforcement-matrix}
# The matrix is an extension of the original analysis. It starts from the same
# orig_rel and synth_rel objects, but retains every prediction family. An inner
# join restricts this extension to directly comparable original/synthetic rows;
# it does not alter the original same-family reinforcement objects above.
original_scores <- orig_all %>%
  filter(is_selected_target(p, Target))

synthetic_scores <- synth_rel %>%
  filter(Pred_Family %in% c("cart", "svm", "parm", "bn")) %>%
  filter(is_selected_target(p, Target)) %>%
  dplyr::select(
    all_of(comparison_keys), synmc, Synthesis_Model, Synth_Family,
    value_synth = Value, rel_synth = rel
  )

comparison <- synthetic_scores %>%
  inner_join(original_scores, by = comparison_keys) %>%
  mutate(
    delta_relative = rel_synth - rel_orig,
    same_family = Synth_Family == Pred_Family
  )

matrix_coverage <- tibble(
  synthetic_rows = nrow(synthetic_scores),
  comparable_rows = nrow(comparison),
  comparable_share = comparable_rows / synthetic_rows
)
print(matrix_coverage)

# Synthesis draws are repeated measurements from the same fitted generator.
# Average before estimating uncertainty.
matrix_unit <- comparison %>%
  group_by(
    Data_Type, p, mc, TargetType, Target, Metric,
    Synthesis_Model, Synth_Family, Pred_Family, same_family
  ) %>%
  summarise(
    rel_orig = first(rel_orig),
    rel_synth = mean(rel_synth),
    delta_relative = mean(delta_relative),
    .groups = "drop")

# Average targets within each independently simulated original dataset.
matrix_cluster <- matrix_unit %>%
  group_by(
    Data_Type, p, mc, TargetType, Metric,
    Synth_Family, Pred_Family, same_family
  ) %>%
  summarise(delta_relative = mean(delta_relative), .groups = "drop")

matrix_summary <- matrix_cluster %>%
  group_by(
    Data_Type, TargetType, Metric,
    Synth_Family, Pred_Family, same_family
  ) %>%
  group_modify(~ bootstrap_mean_summary(.x$delta_relative)) %>%
  ungroup() %>%
  mutate(
    Synth_Family = factor(Synth_Family, levels = family_order),
    Pred_Family = factor(Pred_Family, levels = family_order))

matrix_summary_by_p <- matrix_cluster %>%
  group_by(
    Data_Type, p, TargetType, Metric,
    Synth_Family, Pred_Family, same_family
  ) %>%
  group_modify(~ bootstrap_mean_summary(.x$delta_relative)) %>%
  ungroup()

readr::write_csv(
  matrix_summary,
  file.path(table_dir, "reinforcement_matrix_summary.csv"))
readr::write_csv(
  matrix_summary_by_p,
  file.path(table_dir, "reinforcement_matrix_summary_by_p.csv"))
```

## Matrix heatmaps

```{r matrix-heatmaps, fig.height=8}
plot_reinforcement_matrix <- function(data, target_type) {
  plot_data <- data %>%
    filter(TargetType == target_type) %>%
    mutate(
      Metric = factor(
        Metric,
        levels = if (target_type == "Continuous") {
          continuous_metrics
        } else {
          categorical_metrics
        }))

  if (nrow(plot_data) == 0) {
    message("No matrix observations for ", target_type, "; this plot is skipped.")
    return(NULL)
  }

  fill_limit <- max(abs(plot_data$estimate), na.rm = TRUE)
  ggplot(
    plot_data,
    aes(x = Pred_Family, y = Synth_Family, fill = estimate)
  ) +
    geom_tile(color = "white", linewidth = 0.7) +
    geom_tile(
      data = filter(plot_data, same_family),
      fill = NA, color = "black", linewidth = 1
    ) +
    geom_text(aes(label = sprintf("%+.3f", estimate)), size = 3) +
    facet_grid(
      rows = vars(Metric), cols = vars(Data_Type),
      labeller = labeller(Data_Type = data_type_labels)
    ) +
    scale_x_discrete(labels = family_labels, drop = TRUE) +
    scale_y_discrete(labels = family_labels, drop = TRUE) +
    scale_fill_gradient2(
      low = "#3B6FB6", mid = "white", high = "#C83E4D",
      midpoint = 0, limits = c(-fill_limit, fill_limit),
      name = expression(Delta["relative"])
    ) +
    labs(
      x = "Prediction model",
      y = "Synthesis model"
    ) +
    coord_equal() +
    theme_minimal(base_size = 11) +
    theme(
      legend.position = "bottom",
      panel.grid = element_blank(),
      strip.text = element_text(face = "bold"),
      axis.text.x = element_text(angle = 35, hjust = 1))
}

matrix_plot_continuous <- plot_reinforcement_matrix(matrix_summary, "Continuous")
matrix_plot_categorical <- plot_reinforcement_matrix(matrix_summary, "Categorical")

if (!is.null(matrix_plot_continuous)) {
  ggsave(
    file.path(figure_dir, "reinforcement_matrix_continuous.png"),
    matrix_plot_continuous, width = 5, height = 8, dpi = 300)
  print(matrix_plot_continuous)
}
if (!is.null(matrix_plot_categorical)) {
  ggsave(
    file.path(figure_dir, "reinforcement_matrix_categorical.png"),
    matrix_plot_categorical, width = 5, height = 8, dpi = 300)
  print(matrix_plot_categorical)
}
```

# Diagonal-versus-off-diagonal reinforcement

For each original dataset, target, metric, and synthesis family, define the
diagonal advantage as

\[
A_s = \Delta_{s,s}
- \frac{1}{|\mathcal{M}_s|-1}
  \sum_{m \neq s}\Delta_{s,m}.
\]

Thus, $A_s>0$ means that the matching prediction model improved more than the
average nonmatching model. This directly tests the model-family-specific claim;
it cannot be generated merely because all initially weak models move closer to
the best model.

## Estimate the diagonal advantage

```{r diagonal-contrast}
diagonal_case <- matrix_unit %>%
  group_by(
    Data_Type, p, mc, TargetType, Target, Metric,
    Synthesis_Model, Synth_Family
  ) %>%
  summarise(
    matched_delta = if (sum(same_family) == 1) {
      delta_relative[same_family]
    } else {
      NA_real_
    },
    off_diagonal_delta = mean(delta_relative[!same_family]),
    n_off_diagonal = sum(!same_family),
    diagonal_advantage = matched_delta - off_diagonal_delta,
    .groups = "drop"
  ) %>%
  filter(is.finite(diagonal_advantage))

# Targets and synthesis draws are averaged within each independent original
# simulation dataset. The remaining p-by-mc rows are the bootstrap clusters.
diagonal_cluster <- diagonal_case %>%
  group_by(Data_Type, p, mc, TargetType, Metric, Synth_Family) %>%
  summarise(
    diagonal_advantage = mean(diagonal_advantage),
    .groups = "drop")

diagonal_summary <- diagonal_cluster %>%
  group_by(Data_Type, TargetType, Metric, Synth_Family) %>%
  group_modify(~ bootstrap_mean_summary(.x$diagonal_advantage)) %>%
  ungroup()

# For an overall result, first average metrics within each original dataset so
# that datasets, rather than metrics, determine the effective sample size.
diagonal_overall_cluster <- diagonal_cluster %>%
  group_by(Data_Type, p, mc, TargetType, Synth_Family) %>%
  summarise(
    diagonal_advantage = mean(diagonal_advantage),
    .groups = "drop")

diagonal_overall_summary <- diagonal_overall_cluster %>%
  group_by(Data_Type, TargetType, Synth_Family) %>%
  group_modify(~ bootstrap_mean_summary(.x$diagonal_advantage)) %>%
  ungroup()

readr::write_csv(
  diagonal_summary,
  file.path(table_dir, "diagonal_advantage_by_metric.csv"))
readr::write_csv(
  diagonal_overall_summary,
  file.path(table_dir, "diagonal_advantage_overall.csv"))

diagonal_results_table <- diagonal_overall_summary %>%
  mutate(
    Synthesis_model = dplyr::recode(
      Synth_Family, !!!as.list(family_labels)),
    Data = dplyr::recode(
      Data_Type, !!!as.list(data_type_labels))) %>%
  dplyr::select(
    Data, TargetType, Synthesis_model, n_clusters,
    estimate, conf_low, conf_high, p_boot) %>%
  arrange(Data, TargetType, Synthesis_model)
 
print(diagonal_results_table, n = Inf)
```

## Plot diagonal advantage

```{r diagonal-plot}
diagonal_plot <- diagonal_overall_summary %>%
  mutate(Synth_Family = factor(Synth_Family, levels = family_order)) %>%
  ggplot(aes(x = Synth_Family, y = estimate, color = Synth_Family)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey45") +
  geom_errorbar(
    aes(ymin = conf_low, ymax = conf_high), width = 0.12, linewidth = 0.6
  ) +
  geom_point(size = 2.6) +
  facet_grid(
    rows = vars(TargetType), cols = vars(Data_Type),
    scales = "free_y", labeller = labeller(Data_Type = data_type_labels)
  ) +
  scale_x_discrete(labels = family_labels, drop = TRUE) +
  scale_color_manual(values = family_palette, guide = "none") +
  labs(
    x = "Synthesis model",
    y = "Diagonal advantage"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.spacing.x = grid::unit(1.5, "lines"),
    panel.spacing.y = grid::unit(2, "lines"),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold"),
    axis.text.x = element_text(angle = 35, hjust = 1))

ggsave(
  file.path(figure_dir, "diagonal_advantage.png"),
  diagonal_plot, width = 9, height = 6, dpi = 300)
diagonal_plot
```

## Ceiling-aware random-label cluster permutation analysis
 
The diagonal advantage may be negative when the matching prediction family was
already best on the original data and therefore had no scope to improve, while
other prediction families moved closer to it. Such cases do not provide
negative evidence against same-family reinforcement. We therefore identify
cases in which the matching prediction family was already best and remained
unchanged after synthesis. These ceiling-constrained cases remain part of the
descriptive matrices but are excluded from the following headroom-eligible
inferential analysis.
 
The bootstrap evaluates uncertainty across independently simulated original
datasets. As an additional robustness check, the random-label analysis
designates one prediction family as the focal family within every independent
dataset. The null hypothesis is that the actual diagonal alignment is no more
favorable than an alignment based on a randomly designated focal prediction
family.
 
```{r permutation-test}
best_tolerance <- 1e-8
 
ceiling_case_keys <- c(
  "Data_Type", "p", "mc", "TargetType", "Target", "Metric",
  "Synthesis_Model", "Synth_Family"
)
 
# Identify cases in which the matching prediction family was already best on
# the original data and remained unchanged after synthesis.
diagonal_case_ceiling <- matrix_unit %>%
  group_by(across(all_of(ceiling_case_keys))) %>%
  summarise(
    matched_rel_orig = if (sum(same_family) == 1) {
      rel_orig[same_family]
    } else {
      NA_real_
    },
    matched_delta = if (sum(same_family) == 1) {
      delta_relative[same_family]
    } else {
      NA_real_
    },
    off_diagonal_delta = mean(delta_relative[!same_family]),
    n_off_diagonal = sum(!same_family),
    .groups = "drop"
  ) %>%
  mutate(
    diagonal_advantage = matched_delta - off_diagonal_delta,
    ceiling_constrained =
      matched_rel_orig >= 1 - best_tolerance &
      abs(matched_delta) <= best_tolerance
  ) %>%
  filter(
    is.finite(matched_rel_orig),
    is.finite(matched_delta),
    is.finite(diagonal_advantage)
  )
 
ceiling_summary <- diagonal_case_ceiling %>%
  group_by(Data_Type, TargetType, Synth_Family) %>%
  summarise(
    n_target_metric_cases = n(),
    n_ceiling_cases = sum(ceiling_constrained),
    n_informative_cases = sum(!ceiling_constrained),
    ceiling_share = mean(ceiling_constrained),
    .groups = "drop"
  )
 
readr::write_csv(
  diagonal_case_ceiling,
  file.path(table_dir, "diagonal_ceiling_cases.csv")
)
readr::write_csv(
  ceiling_summary,
  file.path(table_dir, "diagonal_ceiling_summary.csv")
)
 
# Retain all prediction-family rows belonging to non-ceiling cases.
matrix_unit_informative <- matrix_unit %>%
  inner_join(
    diagonal_case_ceiling %>%
      dplyr::select(
        all_of(ceiling_case_keys),
        ceiling_constrained
      ),
    by = ceiling_case_keys
  ) %>%
  filter(!ceiling_constrained)
 
diagonal_case_informative <- diagonal_case_ceiling %>%
  filter(!ceiling_constrained)
 
# Average targets within each metric and independent p-by-mc dataset.
diagonal_metric_cluster_informative <- diagonal_case_informative %>%
  group_by(
    Data_Type, p, mc, TargetType, Metric, Synth_Family
  ) %>%
  summarise(
    diagonal_advantage = mean(diagonal_advantage),
    .groups = "drop"
  )
 
# Average metrics within each independent dataset. Consequently, datasets
# rather than individual targets or metrics determine the effective sample
# size of the bootstrap.
diagonal_cluster_informative <- diagonal_metric_cluster_informative %>%
  group_by(Data_Type, p, mc, TargetType, Synth_Family) %>%
  summarise(
    diagonal_advantage = mean(diagonal_advantage),
    .groups = "drop"
  )
 
diagonal_summary_informative <- diagonal_cluster_informative %>%
  group_by(Data_Type, TargetType, Synth_Family) %>%
  group_modify(
    ~ bootstrap_mean_summary(.x$diagonal_advantage)
  ) %>%
  ungroup()
 
readr::write_csv(
  diagonal_summary_informative,
  file.path(
    table_dir,
    "diagonal_advantage_headroom_eligible.csv"
  )
)
 
# Construct the same p-by-mc analysis units for the random-label analysis.
# Targets are first averaged within metrics and metrics are then averaged
# within each independently generated original dataset.
permutation_metric_cluster <- matrix_unit_informative %>%
  group_by(
    Data_Type, p, mc, TargetType, Metric,
    Synth_Family, Pred_Family
  ) %>%
  summarise(
    delta_relative = mean(delta_relative),
    .groups = "drop"
  )
 
permutation_cluster_data <- permutation_metric_cluster %>%
  group_by(
    Data_Type, p, mc, TargetType,
    Synth_Family, Pred_Family
  ) %>%
  summarise(
    delta_relative = mean(delta_relative),
    .groups = "drop"
  ) %>%
  filter(is.finite(delta_relative))
 
permutation_diagonal_test <- function(data, reps = permutation_reps) {
  cluster_id <- interaction(
    data$p,
    data$mc,
    drop = TRUE,
    lex.order = TRUE
  )
 
  clusters <- split(data, cluster_id)
  clusters <- clusters[vapply(clusters, function(x) {
    nrow(x) >= 2 &&
      sum(x$Pred_Family == x$Synth_Family) == 1 &&
      anyDuplicated(x$Pred_Family) == 0
  }, logical(1))]
 
  if (length(clusters) == 0) {
    return(tibble(
      n_permutation_clusters = 0L,
      observed_advantage = NA_real_,
      null_mean = NA_real_,
      p_one_sided = NA_real_,
      p_two_sided = NA_real_
    ))
  }
 
  cluster_advantage <- function(cluster_data, focal_index) {
    cluster_data$delta_relative[focal_index] -
      mean(cluster_data$delta_relative[-focal_index])
  }
 
  observed <- mean(vapply(clusters, function(cluster_data) {
    matching_index <- which(
      cluster_data$Pred_Family ==
        cluster_data$Synth_Family
    )
    cluster_advantage(cluster_data, matching_index)
  }, numeric(1)))
 
  null_statistics <- replicate(reps, {
    mean(vapply(clusters, function(cluster_data) {
      random_focal_index <- sample.int(
        nrow(cluster_data),
        size = 1
      )
      cluster_advantage(
        cluster_data,
        random_focal_index
      )
    }, numeric(1)))
  })
 
  null_mean <- mean(null_statistics)
 
  tibble(
    n_permutation_clusters = length(clusters),
    observed_advantage = observed,
    null_mean = null_mean,
    p_one_sided =
      (sum(null_statistics >= observed) + 1) /
      (reps + 1),
    p_two_sided = (
      sum(
        abs(null_statistics - null_mean) >=
          abs(observed - null_mean)
      ) + 1
    ) / (reps + 1)
  )
}
 
set.seed(random_seed)
 
permutation_summary <- permutation_cluster_data %>%
  group_by(Data_Type, TargetType, Synth_Family) %>%
  group_modify(
    ~ permutation_diagonal_test(.x),
    .keep = TRUE
  ) %>%
  ungroup()
 
readr::write_csv(
  permutation_summary,
  file.path(
    table_dir,
    "diagonal_permutation_tests.csv"
  )
)
 
# Combine the ceiling information, headroom-eligible bootstrap results, and
# conditional random-label results.
diagonal_inference_summary <- ceiling_summary %>%
  left_join(
    diagonal_summary_informative,
    by = c(
      "Data_Type",
      "TargetType",
      "Synth_Family"
    )
  ) %>%
  left_join(
    permutation_summary,
    by = c(
      "Data_Type",
      "TargetType",
      "Synth_Family"
    )
  ) %>%
  dplyr::select(
    Data_Type,
    TargetType,
    Synth_Family,
    n_target_metric_cases,
    n_ceiling_cases,
    n_informative_cases,
    ceiling_share,
    n_clusters,
    estimate,
    std_error,
    conf_low,
    conf_high,
    n_permutation_clusters,
    observed_advantage,
    null_mean,
    p_one_sided,
    p_two_sided
  )
 
# The bootstrap estimate and observed permutation statistic should agree
# because both use the same headroom-eligible p-by-mc analysis units.
estimate_difference <- abs(
  diagonal_inference_summary$estimate -
    diagonal_inference_summary$observed_advantage
)
 
if (any(estimate_difference > 1e-10, na.rm = TRUE)) {
  warning(
    "The bootstrap estimate and observed permutation statistic do not agree. ",
    "Check the aggregation levels before interpreting the results."
  )
}
 
readr::write_csv(
  diagonal_inference_summary,
  file.path(
    table_dir,
    "diagonal_inference_summary.csv"
  )
)
 
# Classify the conclusions. Fully ceiling-constrained settings are explicitly
# excluded from the assessment of agreement and cannot count as negative
# evidence against the matching-family argument.
inference_agreement <- diagonal_inference_summary %>%
  mutate(
    bootstrap_conclusion = case_when(
      n_informative_cases == 0 ~
        "Ceiling-constrained",
      is.na(conf_low) | is.na(conf_high) ~
        "Not estimable",
      conf_low > 0 ~
        "Positive diagonal advantage",
      conf_high < 0 ~
        "Negative diagonal advantage",
      TRUE ~
        "Inconclusive"
    ),
    permutation_conclusion = case_when(
      n_informative_cases == 0 ~
        "Ceiling-constrained",
      is.na(p_two_sided) |
        is.na(observed_advantage) |
        is.na(null_mean) ~
        "Not estimable",
      p_two_sided < 0.05 &
        observed_advantage > null_mean ~
        "Positive diagonal advantage",
      p_two_sided < 0.05 &
        observed_advantage < null_mean ~
        "Negative diagonal advantage",
      TRUE ~
        "Inconclusive"
    ),
    conclusions_agree = case_when(
      bootstrap_conclusion %in%
        c("Ceiling-constrained", "Not estimable") ~
        NA,
      permutation_conclusion %in%
        c("Ceiling-constrained", "Not estimable") ~
        NA,
      TRUE ~
        bootstrap_conclusion ==
        permutation_conclusion
    )
  )
 
inference_agreement_summary <- inference_agreement %>%
  summarise(
    n_settings = n(),
    n_fully_ceiling_settings =
      sum(n_informative_cases == 0),
    n_evaluable_settings =
      sum(!is.na(conclusions_agree)),
    n_agree =
      sum(conclusions_agree, na.rm = TRUE),
    n_disagree =
      sum(!conclusions_agree, na.rm = TRUE),
    agreement_rate =
      mean(conclusions_agree, na.rm = TRUE)
  )
 
if (
  inference_agreement_summary$n_evaluable_settings == 0
) {
  support_sentence <- paste(
    "The agreement between the random-label and",
    "cluster-bootstrap results could not be evaluated."
  )
} else if (
  inference_agreement_summary$n_disagree == 0
) {
  support_sentence <- paste(
    "The random-label results support the",
    "cluster-bootstrap results across all",
    inference_agreement_summary$n_evaluable_settings,
    "evaluable settings."
  )
} else {
  support_sentence <- paste(
    "The random-label results do not consistently support",
    "the cluster-bootstrap results: the two procedures",
    "yield the same inferential conclusion in",
    inference_agreement_summary$n_agree,
    "of",
    inference_agreement_summary$n_evaluable_settings,
    "evaluable settings."
  )
}
 
total_target_metric_cases <- sum(
  ceiling_summary$n_target_metric_cases
)
total_ceiling_cases <- sum(
  ceiling_summary$n_ceiling_cases
)
 
ceiling_sentence <- paste(
  total_ceiling_cases,
  "of",
  total_target_metric_cases,
  "dataset-target-metric cases are ceiling-constrained.",
  "They remain in the descriptive matrices but are excluded",
  "from the headroom-eligible inferential comparison."
)
 
inference_disagreements <- inference_agreement %>%
  filter(conclusions_agree %in% FALSE) %>%
  dplyr::select(
    Data_Type,
    TargetType,
    Synth_Family,
    n_ceiling_cases,
    n_informative_cases,
    estimate,
    conf_low,
    conf_high,
    p_two_sided,
    bootstrap_conclusion,
    permutation_conclusion
  )
 
readr::write_csv(
  inference_agreement,
  file.path(
    table_dir,
    "diagonal_inference_method_comparison.csv"
  )
)
 
print(ceiling_summary, n = Inf)
print(diagonal_inference_summary, n = Inf)
print(inference_agreement_summary)
cat("\n", ceiling_sentence, "\n", sep = "")
cat("\n", support_sentence, "\n", sep = "")
 
if (nrow(inference_disagreements) > 0) {
  cat(
    "\nSettings with different inferential conclusions:\n"
  )
  print(inference_disagreements, n = Inf)
}
```
 
# Ranking and model-selection analysis
 
The matrix analysis asks how every prediction model moves relative to its
original-data position. The ranking analysis complements it by asking whether
the identity of the selected model or the complete ranking changes.
 
```{r ranking-analysis}
original_rank <- original_scores %>%
  group_by(
    Data_Type,
    p,
    mc,
    TargetType,
    Target,
    Metric
  ) %>%
  mutate(
    rank_orig = case_when(
      first(Metric) %in% higher_better ~
        rank(-value_orig, ties.method = "average"),
      first(Metric) %in% lower_better ~
        rank(value_orig, ties.method = "average")
    ),
    best_orig = rank_orig == min(rank_orig)
  ) %>%
  ungroup() %>%
  dplyr::select(
    all_of(comparison_keys),
    rank_orig,
    best_orig
  )
 
synthetic_rank <- synthetic_scores %>%
  group_by(
    Data_Type,
    p,
    mc,
    synmc,
    Synthesis_Model,
    Synth_Family,
    TargetType,
    Target,
    Metric
  ) %>%
  mutate(
    rank_synth = case_when(
      first(Metric) %in% higher_better ~
        rank(-value_synth, ties.method = "average"),
      first(Metric) %in% lower_better ~
        rank(value_synth, ties.method = "average")
    ),
    best_synth = rank_synth == min(rank_synth)
  ) %>%
  ungroup() %>%
  dplyr::select(
    all_of(comparison_keys),
    synmc,
    Synthesis_Model,
    Synth_Family,
    rank_synth,
    best_synth
  )
 
rank_comparison <- synthetic_rank %>%
  left_join(
    original_rank,
    by = comparison_keys
  )
 
ranking_metrics <- rank_comparison %>%
  group_by(
    Data_Type,
    p,
    mc,
    synmc,
    Synthesis_Model,
    Synth_Family,
    TargetType,
    Target,
    Metric
  ) %>%
  summarise(
    top1_agreement =
      any(best_orig & best_synth, na.rm = TRUE),
    synthetic_best_is_same_family = any(
      best_synth &
        Pred_Family == Synth_Family,
      na.rm = TRUE
    ),
    original_best_is_synth_family = any(
      best_orig &
        Pred_Family == Synth_Family,
      na.rm = TRUE
    ),
    synth_family_rank_orig = dplyr::first(
      rank_orig[Pred_Family == Synth_Family],
      default = NA_real_
    ),
    synth_family_rank_synth = dplyr::first(
      rank_synth[Pred_Family == Synth_Family],
      default = NA_real_
    ),
    spearman_rho = safe_rank_correlation(
      rank_orig,
      rank_synth,
      "spearman"
    ),
    kendall_tau = safe_rank_correlation(
      rank_orig,
      rank_synth,
      "kendall"
    ),
    .groups = "drop"
  ) %>%
  mutate(
    ranking_reversal = !top1_agreement,
    reversal_to_synth_family =
      ranking_reversal &
      synthetic_best_is_same_family,
    synth_family_becomes_winner =
      synthetic_best_is_same_family &
      !original_best_is_synth_family,
    synth_family_rank_change =
      synth_family_rank_synth -
      synth_family_rank_orig
  )
 
ranking_summary <- ranking_metrics %>%
  group_by(
    Synth_Family,
    Synthesis_Model,
    Data_Type,
    p,
    Metric,
    TargetType
  ) %>%
  summarise(
    n_cases = n(),
    n_reversals =
      sum(ranking_reversal, na.rm = TRUE),
    reversal_rate =
      mean(ranking_reversal, na.rm = TRUE),
    n_reversals_to_synth_family =
      sum(
        reversal_to_synth_family,
        na.rm = TRUE
      ),
    share_reversals_to_synth_family =
      if_else(
        n_reversals > 0,
        n_reversals_to_synth_family /
          n_reversals,
        NA_real_
      ),
    n_synth_family_becomes_winner =
      sum(
        synth_family_becomes_winner,
        na.rm = TRUE
      ),
    synth_family_becomes_winner_rate =
      mean(
        synth_family_becomes_winner,
        na.rm = TRUE
      ),
    mean_synth_family_rank_change =
      mean(
        synth_family_rank_change,
        na.rm = TRUE
      ),
    top1_agreement =
      mean(top1_agreement, na.rm = TRUE),
    spearman_rho =
      mean(spearman_rho, na.rm = TRUE),
    kendall_tau =
      mean(kendall_tau, na.rm = TRUE),
    .groups = "drop"
  )
 
ranking_overall <- ranking_metrics %>%
  summarise(
    n_cases = n(),
    n_reversals =
      sum(ranking_reversal, na.rm = TRUE),
    reversal_rate =
      mean(ranking_reversal, na.rm = TRUE),
    n_reversals_to_synth_family =
      sum(
        reversal_to_synth_family,
        na.rm = TRUE
      ),
    share_reversals_to_synth_family =
      if_else(
        n_reversals > 0,
        n_reversals_to_synth_family /
          n_reversals,
        NA_real_
      ),
    n_synth_family_becomes_winner =
      sum(
        synth_family_becomes_winner,
        na.rm = TRUE
      ),
    synth_family_becomes_winner_rate =
      mean(
        synth_family_becomes_winner,
        na.rm = TRUE
      )
  )
 
readr::write_csv(
  ranking_overall,
  file.path(table_dir, "ranking_overall.csv")
)
readr::write_csv(
  ranking_summary,
  file.path(table_dir, "ranking_summary.csv")
)
 
print(ranking_overall)
```
 
# Cases without same-family reinforcement
 
This table identifies cases in which the matching prediction family moves
farther from the best-performing model after synthesis. Cases with a
reinforcement ratio equal to one are not classified as exceptions.
 
```{r exceptions}
reinforcement_exceptions <- same_family_ratio %>%
  filter(reinforcement_ratio < 1) %>%
  dplyr::select(
    Data_Type,
    p,
    mc,
    synmc,
    TargetType,
    Target,
    Metric,
    Synth_Family,
    rel_orig,
    rel_synth,
    reinforcement_ratio
  ) %>%
  arrange(
    Synth_Family,
    Data_Type,
    p,
    mc,
    synmc,
    Target,
    Metric
  )
 
exception_summary <- reinforcement_exceptions %>%
  count(
    Synth_Family,
    Data_Type,
    p,
    TargetType,
    Target,
    Metric,
    name = "n_synthesis_draws"
  ) %>%
  arrange(desc(n_synthesis_draws))
 
readr::write_csv(
  reinforcement_exceptions,
  file.path(
    table_dir,
    "same_family_reinforcement_exceptions.csv"
  )
)
readr::write_csv(
  exception_summary,
  file.path(
    table_dir,
    "same_family_exception_summary.csv"
  )
)
 
print(head(exception_summary, 20), n = 20)
```
 
# Save analysis objects and session information
 
```{r save-results}
saveRDS(
  list(
    comparison = comparison,
    same_family_ratio = same_family_ratio,
    matrix_unit = matrix_unit,
    matrix_summary = matrix_summary,
    diagonal_case = diagonal_case,
    diagonal_summary = diagonal_summary,
    diagonal_overall_summary =
      diagonal_overall_summary,
    diagonal_case_ceiling =
      diagonal_case_ceiling,
    ceiling_summary =
      ceiling_summary,
    matrix_unit_informative =
      matrix_unit_informative,
    diagonal_case_informative =
      diagonal_case_informative,
    diagonal_cluster_informative =
      diagonal_cluster_informative,
    diagonal_summary_informative =
      diagonal_summary_informative,
    permutation_cluster_data =
      permutation_cluster_data,
    permutation_summary =
      permutation_summary,
    diagonal_inference_summary =
      diagonal_inference_summary,
    inference_agreement =
      inference_agreement,
    inference_agreement_summary =
      inference_agreement_summary,
    inference_disagreements =
      inference_disagreements,
    support_sentence =
      support_sentence,
    ceiling_sentence =
      ceiling_sentence,
    ranking_metrics =
      ranking_metrics,
    ranking_summary =
      ranking_summary,
    ranking_overall =
      ranking_overall
  ),
  file.path(
    table_dir,
    "reinforcement_analysis_objects.rds"
  )
)
```
 
# Interpretation guide
 
- **Reinforcement ratio \(R>1\):** the matching prediction model moved closer
  to the best-performing model after synthesis.
- **Reinforcement ratio \(R=1\):** the matching prediction model retained the
  same relative-to-best performance.
- **Matrix cell \(\Delta_{s,m}>0\):** prediction family \(m\) improved relative
  to its original-data position after synthesis by family \(s\).
- **Ceiling-constrained case:** the matching prediction family was already
  best on the original data and remained unchanged after synthesis. Such a
  case is retained descriptively but is not treated as negative evidence.
- **Headroom-eligible diagonal advantage \(A_s>0\):** among cases in which the
  matching model had scope to improve, it improved more than the average
  nonmatching prediction model.
- **Bootstrap interval above zero:** the positive diagonal advantage is
  consistent across independently simulated original datasets.
- **Bootstrap interval below zero:** competing prediction families improve
  more on average in cases not explained by the ceiling constraint.
- **Small two-sided permutation \(p\)-value with a positive observed
  advantage:** the actual diagonal alignment is more favorable than expected
  when the focal prediction family is designated at random.
- **Inconclusive result:** neither procedure distinguishes the observed
  diagonal advantage from zero or from the random-label reference
  distribution.
 
The full matrices and original diagonal contrasts describe all cases,
including those subject to the ceiling constraint. The ceiling-aware
inferential analysis prevents a matching model that was already best and
remained best from being interpreted as negative evidence merely because
competing models subsequently moved closer to it. The reinforcement ratio
remains useful descriptively but, by itself, does not establish that matching
models improve more than all other prediction models.