---
title: "Real_data_prediction"
format: html
editor: visual
---

# Packages

```{r}
# List of required packages
list_of_packages <- c("MASS", "ggplot2", "dplyr", "caret", "rpart", "tidyr", "here", "glmnet" ,"synthpop", "purrr", "MonteCarlo", "tidyverse", "Matrix", "caret", "bnlearn", "e1071", "kernlab", "data.table", "FNN")

# Function to install a package if it is not already installed
install_if_missing <- function(p){
  if(!requireNamespace(p, quietly = TRUE)){
    install.packages(p)
  }
  library(p, character.only=TRUE)
}

# Install and load packages
lapply(list_of_packages, install_if_missing)
```

# Prediction

```{r}
source("Z:/synthetische_Daten/Same_Model_Type_Influence/Simulation/prediction.R")

run_and_save_predictions <- function(syn_obj, target_var, out_dir = "../data/data") {
  if (!is.list(syn_obj) || is.data.frame(syn_obj)) {
    stop("syn_obj must be a list of synthetic datasets.")
  }
  if (!dir.exists(out_dir)) {
    dir.create(out_dir, recursive = TRUE)
  }
  # infer dataset name from object name, e.g. Adult_syn_svm -> Adult
  syn_obj_name <- deparse(substitute(syn_obj))
  dataset_name <- sub("_syn_.*$", "", syn_obj_name)
  pred_funs <- list(
    parm = parm_pred,
    cart = cart_pred,
    bn   = bn_pred,
    svm  = svm_pred
  )
  # rename list elements like dataset1_synmc1 -> synmc1
  old_names <- names(syn_obj)
  new_names <- sub("^.*?(synmc[0-9]+)$", "\\1", old_names)
  invalid_names <- is.na(new_names) | !grepl("synmc[0-9]+$", old_names)
  new_names[invalid_names] <- paste0("synmc", seq_along(syn_obj))[invalid_names]
  names(syn_obj) <- new_names
  all_results <- vector("list", length(syn_obj))
  names(all_results) <- names(syn_obj)
  for (ds_name in names(syn_obj)) {
    dat <- syn_obj[[ds_name]]
    all_results[[ds_name]] <- list()
    for (pred_name in names(pred_funs)) {
      fun <- pred_funs[[pred_name]]
      message("Running prediction for dataset: ", dataset_name,
              " | seed: ", ds_name,
              " | method: ", pred_name)
      res <- tryCatch(
        fun(dat, target_var = target_var),
        error = function(e) {
          message("Error in ", dataset_name, " | ", ds_name,
                  " | ", pred_name, ": ", e$message)
          return(NA)
        }
      )
      # object/file name, e.g. Adult_synmc1_bnpred
      obj_name <- paste0(dataset_name, "_", ds_name, "_", pred_name, "pred")
      assign(obj_name, res)
      save(list = obj_name, file = file.path(out_dir, paste0(obj_name, ".RData")))
      rm(list = obj_name)
      all_results[[ds_name]][[pred_name]] <- res
    }
  }
  return(all_results)
}
```

-   save the preprocessed datasets (original)

-   targets per dataset

-   run each prediction once, specify the target, see how the metric looks for each of the synthesis seeds

-   run prediction once on the original data and 5 times per each synthesis methods (5 synthesis seeds)

## Adult

### On original data

```{r}
load("Z:/synthetische_Daten/Same_Model_Type_Influence/Simulation/real_data/data/data/Adult.RData")

# parm
Adult_orig_parm <- parm_pred(Adult, target_var = "income")
save(Adult_orig_parm, file = "../data/data/Adult_orig_parm.RData")
# cart
Adult_orig_cart <- cart_pred(Adult, target_var = "income")
save(Adult_orig_cart, file = "../data/data/Adult_orig_cart.RData")
# bn
Adult_orig_bn <- bn_pred(Adult, target_var = "income")
save(Adult_orig_bn, file = "../data/data/Adult_orig_bn.RData")
# svm
Adult_orig_svm <- svm_pred(Adult, target_var = "income")
save(Adult_orig_svm, file = "../data/data/Adult_orig_svm.RData")

```

### On parametrically synthesized data

```{r}
Adult_parmsyn <- get(load("../data/data/Adult_syn_parm.RData"))
run_and_save_predictions(Adult_parmsyn, "income")
```

### On CART-synthesized data

```{r}
Adult_cartsyn <- get(load("../data/data/Adult_syn_cart.RData"))
run_and_save_predictions(Adult_cartsyn, "income")
```

### On BN-synthesized data

```{r}
Adult_bnsyn <- get(load("../data/data/Adult_syn_bn.RData"))
run_and_save_predictions(Adult_bnsyn, "income")
```

### On SVM-synthesized data

```{r}
Adult_svmsyn <- get(load("../data/data/Adult_syn_svm.RData"))
run_and_save_predictions(Adult_svmsyn, "income")
```

## Bank and Marketing

### On original data

```{r}
load("Z:/synthetische_Daten/Same_Model_Type_Influence/Simulation/real_data/data/data/BankMarketing.RData")  
# parm 
BankMarketing_orig_parm <- parm_pred(BankMarketing, target_var = "y")
save(BankMarketing_orig_parm, file = "../data/data/BankMarketing_orig_parm.RData") 
# cart 
BankMarketing_orig_cart <- cart_pred(BankMarketing, target_var = "y") 
save(BankMarketing_orig_cart, file = "../data/data/BankMarketing_orig_cart.RData") 
# bn 
BankMarketing_orig_bn <- bn_pred(BankMarketing, target_var = "y") 
save(BankMarketing_orig_bn, file = "../data/data/BankMarketing_orig_bn.RData") 
# svm 
BankMarketing_orig_svm <- svm_pred(BankMarketing, target_var = "y") 
save(BankMarketing_orig_svm, file = "../data/data/BankMarketing_orig_svm.RData") 
```

### On parametricly synthesized data

```{r}
BankMarketing_parmsyn <- get(load("../data/data/BankMarketing_syn_parm.RData"))  
run_and_save_predictions(BankMarketing_parmsyn, "y")
```

### On CART-synthesized data

```{r}
BankMarketing_cartsyn <- get(load("../data/data/BankMarketing_syn_cart.RData"))  
run_and_save_predictions(BankMarketing_cartsyn, "y")
```

### On BN-synthesized data

```{r}
BankMarketing_bnsyn <- get(load("../data/data/BankMarketing_syn_bn.RData"))
run_and_save_predictions(BankMarketing_bnsyn, "y")
```

### On SVM-synthesized data

```{r}
BankMarketing_svmsyn <- get(load("../data/data/BankMarketing_syn_svm.RData"))
run_and_save_predictions(BankMarketing_svmsyn, "y")
```

## Bike Sharing

### On original data

```{r}
load("Z:/synthetische_Daten/Same_Model_Type_Influence/Simulation/real_data/data/data/BikeSharing.RData")  
# parm 
BikeSharing_orig_parm <- parm_pred(BikeSharing, target_var = "cnt")
save(BikeSharing_orig_parm, file = "../data/data/BikeSharing_orig_parm.RData") 
# cart 
BikeSharing_orig_cart <- cart_pred(BikeSharing, target_var = "cnt") 
save(BikeSharing_orig_cart, file = "../data/data/BikeSharing_orig_cart.RData") 
# bn 
BikeSharing_orig_bn <- bn_pred(BikeSharing, target_var = "cnt") 
save(BikeSharing_orig_bn, file = "../data/data/BikeSharing_orig_bn.RData") 
# svm 
BikeSharing_orig_svm <- svm_pred(BikeSharing, target_var = "cnt") 
save(BikeSharing_orig_svm, file = "../data/data/BikeSharing_orig_svm.RData")
```

### On parametricly synthesized data

```{r}
BikeSharing_parmsyn <- get(load("../data/data/BikeSharing_syn_parm.RData"))  
run_and_save_predictions(BikeSharing_parmsyn, "cnt")
```

### On CART-synthesized data

```{r}
BikeSharing_cartsyn <- get(load("../data/data/BikeSharing_syn_cart.RData"))  
run_and_save_predictions(BikeSharing_cartsyn, "cnt")
```

### On BN-synthesized data

```{r}
BikeSharing_bnsyn <- get(load("../data/data/BikeSharing_syn_bn.RData"))
run_and_save_predictions(BikeSharing_bnsyn, "cnt")
```

### On SVM-synthesized data

```{r}
BikeSharing_svmsyn <- get(load("../data/data/BikeSharing_syn_svm.RData"))
run_and_save_predictions(BikeSharing_svmsyn, "cnt")
```

## German Credit

### On original data

```{r}
load("Z:/synthetische_Daten/Same_Model_Type_Influence/Simulation/real_data/data/data/GermanCredit.RData")
# parm  
GermanCredit_orig_parm <- parm_pred(GermanCredit, target_var = "class") 
save(GermanCredit_orig_parm, file = "../data/data/GermanCredit_orig_parm.RData")  
# cart  
GermanCredit_orig_cart <- cart_pred(GermanCredit, target_var = "class")  
save(GermanCredit_orig_cart, file = "../data/data/GermanCredit_orig_cart.RData")  
# bn  
GermanCredit_orig_bn <- bn_pred(GermanCredit, target_var = "class")  
save(GermanCredit_orig_bn, file = "../data/data/GermanCredit_orig_bn.RData")  
# svm  
GermanCredit_orig_svm <- svm_pred(GermanCredit, target_var = "class")  
save(GermanCredit_orig_svm, file = "../data/data/GermanCredit_orig_svm.RData")
```

### On parametricly synthesized data

```{r}
GermanCredit_parmsyn <- get(load("../data/data/GermanCredit_syn_parm.RData"))  
run_and_save_predictions(GermanCredit_parmsyn, "class")
```

### On CART-synthesized data

```{r}
GermanCredit_cartsyn <- get(load("../data/data/GermanCredit_syn_cart.RData"))  
run_and_save_predictions(GermanCredit_cartsyn, "class")
```

### On BN-synthesized data

```{r}
GermanCredit_bnsyn <- get(load("../data/data/GermanCredit_syn_bn.RData"))
run_and_save_predictions(GermanCredit_bnsyn, "class")
```

### On SVM-synthesized data

```{r}
GermanCredit_svmsyn <- get(load("../data/data/GermanCredit_syn_svm.RData"))
run_and_save_predictions(GermanCredit_svmsyn, "class")
```
