---
title: "pred_on_sim"
output: html_document
date: "2026-09-21"
---
 
# Packages
 
```{r}
list_of_packages <- c(
  "MASS", "ggplot2", "dplyr", "caret", "rpart", "tidyr", "here",
  "glmnet", "synthpop", "purrr", "MonteCarlo", "tidyverse", "Matrix",
  "e1071", "bnlearn", "future", "furrr", "kernlab")
 
install_if_missing <- function(p) {
  if (!requireNamespace(p, quietly = TRUE)) install.packages(p)
  library(p, character.only = TRUE)
}
 
invisible(lapply(unique(list_of_packages), install_if_missing))
```
 
# Load data
 
```{r}
sim_hierarchical <- readRDS(here::here("data", "sim_hierarchical.rds"))
sim_linear <- readRDS(here::here("data", "sim_linear.rds"))
 
cat("Hierarchical simulation datasets:", length(sim_hierarchical), "\n")
cat("Linear simulation datasets:", length(sim_linear), "\n")
```
 
# Load functions
 
```{r}
source(here::here("code", "prediction.R"))
```
 
# Settings
 
```{r}
workers <- 8
 
# Predictor restrictions
restrict_hier <- FALSE
restrict_linear <- TRUE
 
# Expected number of original datasets:
# 3 p-values x 5 simulation replications = 15
expected_n <- 3 * 5
 
if (length(sim_hierarchical) != expected_n) {
  warning(
    "sim_hierarchical contains ", length(sim_hierarchical),
    " datasets; expected ", expected_n, ".")
}
 
if (length(sim_linear) != expected_n) {
  warning(
    "sim_linear contains ", length(sim_linear),
    " datasets; expected ", expected_n, ".")
}
```
 
# Apply predictions
 
## Parametric prediction
 
### Hierarchical simulation
 
```{r}
parmpred_hiersim <- run_prediction_grid(
  data_object = sim_hierarchical,
  prediction_function = parm_pred,
  output_file = "parmpred_hiersim",
  restrict_predictors = restrict_hier,
  workers = workers)
```
 
### Linear simulation
 
```{r}
parmpred_linsim <- run_prediction_grid(
  data_object = sim_linear,
  prediction_function = parm_pred,
  output_file = "parmpred_linsim",
  restrict_predictors = restrict_linear,
  workers = workers)
```
 
## CART prediction
 
### Hierarchical simulation
 
```{r}
cartpred_hiersim <- run_prediction_grid(
  data_object = sim_hierarchical,
  prediction_function = cart_pred,
  output_file = "cartpred_hiersim",
  restrict_predictors = restrict_hier,
  workers = workers)
```
 
### Linear simulation
 
```{r}
cartpred_linsim <- run_prediction_grid(
  data_object = sim_linear,
  prediction_function = cart_pred,
  output_file = "cartpred_linsim",
  restrict_predictors = restrict_linear,
  workers = workers)
```
 
## Bayesian Network prediction
 
### Hierarchical simulation
 
```{r}
bnpred_hiersim <- run_prediction_grid(
  data_object = sim_hierarchical,
  prediction_function = bn_pred,
  output_file = "bnpred_hiersim",
  restrict_predictors = restrict_hier,
  workers = workers)
```
 
### Linear simulation
 
```{r}
bnpred_linsim <- run_prediction_grid(
  data_object = sim_linear,
  prediction_function = bn_pred,
  output_file = "bnpred_linsim",
  restrict_predictors = restrict_linear,
  workers = workers)
```
 
## SVM prediction
 
### Hierarchical simulation
 
```{r}
svmpred_hiersim <- run_prediction_grid(
  data_object = sim_hierarchical,
  prediction_function = svm_pred,
  output_file = "svmpred_hiersim",
  restrict_predictors = restrict_hier,
  workers = workers)
```
 
### Linear simulation
 
```{r}
svmpred_linsim <- run_prediction_grid(
  data_object = sim_linear,
  prediction_function = svm_pred,
  output_file = "svmpred_linsim",
  restrict_predictors = restrict_linear,
  workers = workers)
```
 
# Validate outputs
 
```{r}
prediction_objects <- c(
  "parmpred_hiersim", "parmpred_linsim",
  "cartpred_hiersim", "cartpred_linsim",
  "bnpred_hiersim", "bnpred_linsim",
  "svmpred_hiersim", "svmpred_linsim")
 
for (obj in prediction_objects) {
  if (!exists(obj)) {
    warning(obj, " does not exist.")
    next
  }
 
  x <- get(obj)
  if (length(x) != expected_n) {
    warning(
      obj, " contains ", length(x),
      " results; expected ", expected_n, ".")
  } else {
    cat(obj, ":", length(x), "results -- OK\n")
  }
}
```
 
# Reset parallel backend
 
```{r}
future::plan(future::sequential)
```