---
title: "Real-Data Prediction"
format: html
editor: visual
---

# Packages

```{r packages}
list_of_packages <- c(
  "MASS", "ggplot2", "dplyr", "caret", "rpart", "tidyr", "here",
  "glmnet", "synthpop", "purrr", "MonteCarlo", "tidyverse", "Matrix",
  "bnlearn", "e1071", "kernlab", "data.table", "FNN")

install_if_missing <- function(p) {
  if (!requireNamespace(p, quietly = TRUE)) install.packages(p)
  library(p, character.only = TRUE)
}

invisible(lapply(list_of_packages, install_if_missing))
```

# Setup

```{r setup}
data_dir <- here::here("data", "real_data", "data")
dir.create(data_dir, recursive = TRUE, showWarnings = FALSE)

source(here::here("code", "prediction.R"))

prediction_functions <- list(
  parm = parm_pred,
  cart = cart_pred,
  bn = bn_pred,
  svm = svm_pred)
```

# Helper functions

```{r helper-functions}
load_single_object <- function(path) {
  if (!file.exists(path)) stop("Required file not found: ", path)

  load_env <- new.env(parent = emptyenv())
  object_names <- load(path, envir = load_env)

  if (length(object_names) != 1) {
    stop("Expected exactly one object in ", path, "; found ",
         length(object_names), ".")
  }

  load_env[[object_names]]
}

save_named_result <- function(result, object_name, out_dir = data_dir) {
  save_env <- new.env(parent = emptyenv())
  assign(object_name, result, envir = save_env)
  output_path <- file.path(out_dir, paste0(object_name, ".RData"))
  save(list = object_name, file = output_path, envir = save_env)
  message("Saved: ", output_path)
  invisible(output_path)
}

run_original_predictions <- function(
    data, dataset_name, target_var,
    prediction_methods = names(prediction_functions), out_dir = data_dir) {

  invalid_methods <- setdiff(prediction_methods, names(prediction_functions))
  if (length(invalid_methods) > 0) {
    stop("Unknown prediction method(s): ",
         paste(invalid_methods, collapse = ", "))
  }

  results <- setNames(vector("list", length(prediction_methods)),
                      prediction_methods)

  for (pred_name in prediction_methods) {
    message("Running original-data prediction: ", dataset_name,
            " | method: ", pred_name)

    result <- prediction_functions[[pred_name]](
      data, target_var = target_var)
    object_name <- paste0(dataset_name, "_orig_", pred_name)
    save_named_result(result, object_name, out_dir)
    results[[pred_name]] <- result
  }

  invisible(results)
}

run_synthetic_predictions <- function(
    syn_obj, target_var, output_prefix,
    prediction_methods = names(prediction_functions), out_dir = data_dir) {

  if (!is.list(syn_obj) || is.data.frame(syn_obj)) {
    stop("syn_obj must be a list of synthetic datasets.")
  }

  invalid_methods <- setdiff(prediction_methods, names(prediction_functions))
  if (length(invalid_methods) > 0) {
    stop("Unknown prediction method(s): ",
         paste(invalid_methods, collapse = ", "))
  }

  old_names <- names(syn_obj)
  if (is.null(old_names)) old_names <- rep("", length(syn_obj))

  new_names <- sub("^.*?(synmc[0-9]+)$", "\\1", old_names)
  invalid_names <- !grepl("synmc[0-9]+$", old_names)
  new_names[invalid_names] <- paste0("synmc", seq_along(syn_obj))[invalid_names]

  if (anyDuplicated(new_names)) {
    stop("Synthetic-dataset names cannot be mapped uniquely to synmc identifiers.")
  }

  names(syn_obj) <- new_names
  all_results <- setNames(vector("list", length(syn_obj)), new_names)

  for (syn_name in new_names) {
    data <- syn_obj[[syn_name]]
    all_results[[syn_name]] <- setNames(
      vector("list", length(prediction_methods)), prediction_methods)

    for (pred_name in prediction_methods) {
      message("Running synthetic-data prediction: ", output_prefix,
              " | seed: ", syn_name, " | method: ", pred_name)

      result <- prediction_functions[[pred_name]](
        data, target_var = target_var)
      object_name <- paste0(
        output_prefix, "_", syn_name, "_", pred_name, "pred")
      save_named_result(result, object_name, out_dir)
      all_results[[syn_name]][[pred_name]] <- result
    }
  }

  invisible(all_results)
}
```

# Adult

## Original data

```{r adult-original}
Adult <- load_single_object(file.path(data_dir, "Adult.RData"))
Adult_orig_results <- run_original_predictions(
  Adult, dataset_name = "Adult", target_var = "income")
```

## Parametric synthetic data

```{r adult-parametric}
Adult_parmsyn <- load_single_object(file.path(data_dir, "Adult_syn_parm.RData"))
Adult_parmsyn_results <- run_synthetic_predictions(
  Adult_parmsyn, target_var = "income", output_prefix = "Adult_parmsyn")
```

## CART synthetic data

```{r adult-cart}
Adult_cartsyn <- load_single_object(file.path(data_dir, "Adult_syn_cart.RData"))
Adult_cartsyn_results <- run_synthetic_predictions(
  Adult_cartsyn, target_var = "income", output_prefix = "Adult_cartsyn")
```

## Bayesian-network synthetic data

```{r adult-bn}
Adult_bnsyn <- load_single_object(file.path(data_dir, "Adult_syn_bn.RData"))
Adult_bnsyn_results <- run_synthetic_predictions(
  Adult_bnsyn, target_var = "income", output_prefix = "Adult_bnsyn")
```

## SVM synthetic data

```{r adult-svm}
Adult_svmsyn <- load_single_object(file.path(data_dir, "Adult_syn_svm.RData"))
Adult_svmsyn_results <- run_synthetic_predictions(
  Adult_svmsyn, target_var = "income", output_prefix = "Adult_svmsyn")
```

# Bank Marketing

## Original data

```{r bank-original}
BankMarketing <- load_single_object(file.path(data_dir, "BankMarketing.RData"))
BankMarketing_orig_results <- run_original_predictions(
  BankMarketing, dataset_name = "BankMarketing", target_var = "y")
```

## Parametric synthetic data

```{r bank-parametric}
BankMarketing_parmsyn <- load_single_object(file.path(data_dir, "BankMarketing_syn_parm.RData"))
BankMarketing_parmsyn_results <- run_synthetic_predictions(
  BankMarketing_parmsyn, target_var = "y",
  output_prefix = "BankMarketing_parmsyn")
```

## CART synthetic data

```{r bank-cart}
BankMarketing_cartsyn <- load_single_object(file.path(data_dir, "BankMarketing_syn_cart.RData"))
BankMarketing_cartsyn_results <- run_synthetic_predictions(
  BankMarketing_cartsyn, target_var = "y",
  output_prefix = "BankMarketing_cartsyn")
```

## Bayesian-network synthetic data

```{r bank-bn}
BankMarketing_bnsyn <- load_single_object(file.path(data_dir, "BankMarketing_syn_bn.RData"))
BankMarketing_bnsyn_results <- run_synthetic_predictions(
  BankMarketing_bnsyn, target_var = "y",
  output_prefix = "BankMarketing_bnsyn")
```

## SVM synthetic data

```{r bank-svm}
BankMarketing_svmsyn <- load_single_object(file.path(data_dir, "BankMarketing_syn_svm.RData"))
BankMarketing_svmsyn_results <- run_synthetic_predictions(
  BankMarketing_svmsyn, target_var = "y",
  output_prefix = "BankMarketing_svmsyn")
```

# Bike Sharing

Bayesian-network prediction and synthesis are excluded for this regression target, consistently with the downstream analysis.

## Original data

```{r bike-original}
regression_methods <- c("parm", "cart", "svm")

BikeSharing <- load_single_object(file.path(data_dir, "BikeSharing.RData"))
BikeSharing_orig_results <- run_original_predictions(
  BikeSharing, dataset_name = "BikeSharing", target_var = "cnt",
  prediction_methods = regression_methods)
```

## Parametric synthetic data

```{r bike-parametric}
BikeSharing_parmsyn <- load_single_object(file.path(data_dir, "BikeSharing_syn_parm.RData"))
BikeSharing_parmsyn_results <- run_synthetic_predictions(
  BikeSharing_parmsyn, target_var = "cnt",
  output_prefix = "BikeSharing_parmsyn",
  prediction_methods = regression_methods)
```

## CART synthetic data

```{r bike-cart}
BikeSharing_cartsyn <- load_single_object(file.path(data_dir, "BikeSharing_syn_cart.RData"))
BikeSharing_cartsyn_results <- run_synthetic_predictions(
  BikeSharing_cartsyn, target_var = "cnt",
  output_prefix = "BikeSharing_cartsyn",
  prediction_methods = regression_methods)
```

## SVM synthetic data

```{r bike-svm}
BikeSharing_svmsyn <- load_single_object(file.path(data_dir, "BikeSharing_syn_svm.RData"))
BikeSharing_svmsyn_results <- run_synthetic_predictions(
  BikeSharing_svmsyn, target_var = "cnt",
  output_prefix = "BikeSharing_svmsyn",
  prediction_methods = regression_methods)
```

# German Credit

## Original data

```{r german-original}
GermanCredit <- load_single_object(file.path(data_dir, "GermanCredit.RData"))
GermanCredit_orig_results <- run_original_predictions(
  GermanCredit, dataset_name = "GermanCredit", target_var = "class")
```

## Parametric synthetic data

```{r german-parametric}
GermanCredit_parmsyn <- load_single_object(file.path(data_dir, "GermanCredit_syn_parm.RData"))
GermanCredit_parmsyn_results <- run_synthetic_predictions(
  GermanCredit_parmsyn, target_var = "class",
  output_prefix = "GermanCredit_parmsyn")
```

## CART synthetic data

```{r german-cart}
GermanCredit_cartsyn <- load_single_object(file.path(data_dir, "GermanCredit_syn_cart.RData"))
GermanCredit_cartsyn_results <- run_synthetic_predictions(
  GermanCredit_cartsyn, target_var = "class",
  output_prefix = "GermanCredit_cartsyn")
```

## Bayesian-network synthetic data

```{r german-bn}
GermanCredit_bnsyn <- load_single_object(file.path(data_dir, "GermanCredit_syn_bn.RData"))
GermanCredit_bnsyn_results <- run_synthetic_predictions(
  GermanCredit_bnsyn, target_var = "class",
  output_prefix = "GermanCredit_bnsyn")
```

## SVM synthetic data

```{r german-svm}
GermanCredit_svmsyn <- load_single_object(file.path(data_dir, "GermanCredit_syn_svm.RData"))
GermanCredit_svmsyn_results <- run_synthetic_predictions(
  GermanCredit_svmsyn, target_var = "class",
  output_prefix = "GermanCredit_svmsyn")
```

# Validation

```{r validation}
expected_files <- c(
  unlist(lapply(c("Adult", "BankMarketing", "GermanCredit"), function(dataset) {
    c(
      paste0(dataset, "_orig_", names(prediction_functions), ".RData"),
      unlist(lapply(c("parmsyn", "cartsyn", "bnsyn", "svmsyn"),
                    function(synth_method) {
        paste0(dataset, "_", synth_method, "_synmc", 1:5, "_",
               rep(names(prediction_functions), each = 5), "pred.RData")
      })))
  })),
  paste0("BikeSharing_orig_", regression_methods, ".RData"),
  unlist(lapply(c("parmsyn", "cartsyn", "svmsyn"), function(synth_method) {
    paste0("BikeSharing_", synth_method, "_synmc", 1:5, "_",
           rep(regression_methods, each = 5), "pred.RData")
  })))

missing_files <- expected_files[
  !file.exists(file.path(data_dir, expected_files))]

if (length(missing_files) > 0) {
  warning(length(missing_files), " expected prediction files are missing:\n",
          paste(missing_files, collapse = "\n"))
} else {
  cat("All", length(expected_files), "expected prediction files are present.\n")
}
```
