---
title: "pred_on_svmsyn"
output: html_document
date: "2026-09-16"
---
 
# Packages
```{r}
 
# List of required packages
list_of_packages <- c("MASS", "ggplot2", "dplyr", "caret", "rpart", "tidyr", "here", "glmnet" ,"synthpop", "purrr", "MonteCarlo", "tidyverse", "Matrix", "caret", "e1071", "bnlearn", "future", "furrr", "kernlab")
 
# Function to install a package if it is not already installed
install_if_missing <- function(p){
  if(!requireNamespace(p, quietly = TRUE)){install.packages(p)}
  library(p, character.only=TRUE)}
 
# Install and load packages
lapply(list_of_packages, install_if_missing)
 
```
 
# Load data
```{r}
load(here::here("data", "svm_hiersyn.RData"))
load(here::here("data", "svm_linsyn.RData"))
 
cat("Hierarchical SVM synthetic datasets:", length(svm_hiersyn), "\n")
cat("Linear SVM synthetic datasets:", length(svm_linsyn), "\n")
```
 
# Load functions
 
```{r}
source(here::here("code", "prediction.R"))
```
 
# Settings
 
```{r}
 
workers <- 4
 
# Predictor restrictions
restrict_hier <- FALSE
restrict_linear <- TRUE
 
# Expected number of synthetic datasets:
# 3 p-values x 5 simulation replications x 5 synthesis replications = 75
expected_n <- 3 * 5 * 5
 
if (length(svm_hiersyn) != expected_n) {
  warning("svm_hiersyn contains ", length(svm_hiersyn),
          " datasets; expected ", expected_n, ".")
}
 
if (length(svm_linsyn) != expected_n) {
  warning("svm_linsyn contains ", length(svm_linsyn),
          " datasets; expected ", expected_n, ".")
}
 
```
 
# Apply predictions
 
## Parametric prediction
 
### Hierarchical simulation
```{r}
parmpred_svmhiersyn <- run_prediction_grid(
  data_object = svm_hiersyn,
  prediction_function = parm_pred,
  output_file = "parmpred_svmhiersyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_hier,
  workers = workers)
 
```
 
### Parametric simulation
```{r}
parmpred_svmlinsyn <- run_prediction_grid(
  data_object = svm_linsyn,
  prediction_function = parm_pred,
  output_file = "parmpred_svmlinsyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_linear,
  workers = workers)
 
```
 
## CART prediction
 
### Hierarchical simulation
```{r}
cartpred_svmhiersyn <- run_prediction_grid(
  data_object = svm_hiersyn,
  prediction_function = cart_pred,
  output_file = "cartpred_svmhiersyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_hier,
  workers = workers)
 
```
 
### Parametric simulation
```{r}
cartpred_svmlinsyn <- run_prediction_grid(
  data_object = svm_linsyn,
  prediction_function = cart_pred,
  output_file = "cartpred_svmlinsyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_linear,
  workers = workers)
 
```
 
## Bayesian Network prediction
 
### Hierarchical simulation
```{r}
bnpred_svmhiersyn <- run_prediction_grid(
  data_object = svm_hiersyn,
  prediction_function = bn_pred,
  output_file = "bnpred_svmhiersyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_hier,
  workers = workers)
 
```
 
### Parametric simulation
```{r}
bnpred_svmlinsyn <- run_prediction_grid(
  data_object = svm_linsyn,
  prediction_function = bn_pred,
  output_file = "bnpred_svmlinsyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_linear,
  workers = workers)
 
```
 
## SVM prediction
 
### Hierarchical simulation
```{r}
svmpred_svmhiersyn <- run_prediction_grid(
  data_object = svm_hiersyn,
  prediction_function = svm_pred,
  output_file = "svmpred_svmhiersyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_hier,
  workers = workers)
 
```
 
### Parametric simulation
```{r}
svmpred_svmlinsyn <- run_prediction_grid(
  data_object = svm_linsyn,
  prediction_function = svm_pred,
  output_file = "svmpred_svmlinsyn",
  synmc_values = 1:5,
  restrict_predictors = restrict_linear,
  workers = workers)
 
```
 
# Validate outputs
```{r}
prediction_objects <- c(
  "parmpred_svmhiersyn",
  "parmpred_svmlinsyn",
  "cartpred_svmhiersyn",
  "cartpred_svmlinsyn",
  "bnpred_svmhiersyn",
  "bnpred_svmlinsyn",
  "svmpred_svmhiersyn",
  "svmpred_svmlinsyn"
)
 
for (obj in prediction_objects) {
 
  if (!exists(obj)) {
    warning(obj, " does not exist.")
    next
  }
 
  x <- get(obj)
 
  if (length(x) != expected_n) {
    warning(
      obj, " contains ", length(x),
      " results; expected ", expected_n, "."
    )
  } else {
    cat(obj, ":", length(x), "results -- OK\n")
  }
}
 
```
 
# Reset parallel backend
```{r}
future::plan(future::sequential)
```